---
title: Analyses of species distributions in peatlands
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Load the R packages that you will use

If you do not have the R packages installed, you need to install them. 

```{r load packages}
library(tidyverse)
library(readxl)
library(knitr)
library(ggeffects)
library(car)
library(glmmTMB)
library(ggplot2)
library(BiodiversityR)
library(vegan)
library(rdacca.hp)
```

# Data preparation

## Read data from Excel file

Note that you need to change the path to the folder where you have the Excel file

```{r}
data_peat<-read_excel("data/raw/Modelling_SDM_species_data_Updated.xlsx",
                      sheet="Sheet1")
data_peat<-data_peat[1:29] # This is to remove some columns that we do not need!
```

## Have a look at the data

This shows the first rows of your data file in "tibble" format. You can also see the variable type for each variable (double or character).

```{r}
data_peat
```

## Convert some variables to factors

It is better to convert some variables (those that are Y/N or 0/1) to factors.

```{r}
data_peat<-data_peat%>%
  mutate(fen=as.factor(fen),imp_temp=as.factor(imp_temp),
         nutrient=as.factor(nutrient),fire=as.factor(fire),dry=as.factor(dry)) 
# with mutate you create new variables that are equal to the old variables
# but are coded as factors
```

## Convert moist to numeric

For some reason, moist appears as a character variable. It should be numeric, so we convert it.

```{r}
data_peat<-data_peat%>%
  mutate(moist=as.numeric(moist))
```

# Ordinations (vegan package)

Suggested reading: https://www.davidzeleny.net/anadat-r/doku.php/en:ordination

(lots of info on this webpage!)

Chapter 10 in this pdf: https://apps.worldagroforestry.org/downloads/Publications/PDFS/b13695.pdf

Using the vegan package.

I performed some ordinations with Sphagnum species. I tried different methods, but if I would need to choose one, I would do a constrained ordination, specifically a Distance-based redundancy analysis (db-RDA) with Bray-Curtis distance. You can read about all types in the webpage above if you feel like it. 

Data for ordination: 

```{r}
data_ordi2<-data_peat %>%
  filter_at(vars(Balticum:Fallax), 
            all_vars(!is.na(.)))%>% # Remove rows with all NAs
  filter_at(vars(Balticum:Fallax),
            any_vars(.>0))%>% # Remove rows with all zeros - WHY?
  filter(!is.na(age)&!is.na(temp)&!is.na(moist)&!is.na(nutrient)&!is.na(fire)&
           !is.na(dry))%>% # Remove rows with NA in predictors
  rename(Deformed_Acutifolia=`Diseased Acutifolia`) #Rename to avoid problems
```

Distance-based redundancy analysis (db-RDA) with Bray-Curtis distance.

See https://www.davidzeleny.net/anadat-r/doku.php/en:similarity for info on distances.

Calculate ordination:

```{r}
ordi6<-capscale(data_ordi2[10:21]~ # species data matrix
             age+temp+moist+nutrient+fire+dry, # Environmental variables
             data = data_ordi2, distance="bray") # Bray-Curtis distance

```

Result of the ordination:

```{r}
ordi6
```

"Intertia" is the total variance - your environmental variables explain 0.2704 of this variance ("constrained" part).

Proportion explained by each ordination axis. CAP1-CAP6 are the "constrained" axes, explained by your environmental variables. MDS1-MDS34 are the "unconstrained" axes.

```{r}
eigenvals(ordi6) %>%
  summary()
```

Barplot of percentage variance explained by individual axes

```{r}
expl_var_ordi6 <- c(ordi6$CCA$eig/ordi6$tot.chi*100, 
                    ordi6$CA$eig/ordi6$tot.chi*100)
barplot (expl_var_ordi6, col = c(rep ('red', 
                                      length (ordi6$CCA$eig/ordi6$tot.chi*100)), 
                                 rep ('black', 
                                      length (ordi6$CA$eig/ordi6$tot.chi*100))),
         las = 2, ylab = '% variation')
```

Plot of the ordination (species in red and sites-samples in black):

```{r fig.height=6, fig.width=6}
vegan::ordiplot(ordi6,display = c('species', 'sites', 'bp'))
orditorp(ordi6,display="species",cex=0.8,col="red")
```

This shows the two first constrained axes of the ordination. You can see how the sites and species distribute along these axes.

Test significance of the ordination with Monte Carlo permutation test.

For the whole model:

```{r}
anova (ordi6, permutations = 999) 
```

The model is significant.

For each explanatory variable (with all the others used as covariables, independently from their order in the model):

```{r}
anova (ordi6, by = 'margin', permutations = 999)
```

Age, moist, nutrient and dry show significant effects.

For each axis:

```{r}
anova (ordi6, by = 'axis', permutations = 999)
```

Axis 1 and 2 are significant.

Ordination plot with ggplot2.

Install ggord package (you only need to do this once):

```{r}
# Enable the r-universe repo
options(repos = c(
    fawda123 = 'https://fawda123.r-universe.dev',
    CRAN = 'https://cloud.r-project.org'))

# Install ggord
install.packages('ggord')
```

Load ggord package:

```{r}
library(ggord)
```


```{r}
ggord(ordi6,ptslab=T,repel=T,labcol="red",veccol="red",size=NA,addsize=3,
      xlims=c(-1.1,1.1),ylims=c(-1.1,1.1))+
  geom_point(size=3,shape=20,color="black",alpha=0.2)
```

## Hierarchical partitioning

```{r}
dist_matrix<-vegdist(data_ordi2[10:21],method="bray")
```

```{r}
hierpart1<-rdacca.hp(dist_matrix,data_ordi2[c(23:24,26:29)],method = "dbRDA",
          type ="adjR2",scale = F,add = T,sqrt.dist = T)
hierpart1
plot(hierpart1,plot.perc=T)
```

```{r}
cor(data_ordi2[c(23:24)]) # Correlation among age and temp is 0.762
vif.cca(ordi6)
# But VIF of the ordination is not super high, probably ok to keep both
```

