---
title: Analyses of species distributions in peatlands - SHORT
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Load the R packages that you will use

If you do not have the R packages installed, you need to install them. 

```{r load packages}
library(readxl)
library(tidyverse)
library(glmmTMB)
library(performance)
```

# Data preparation

## Read data from Excel file

Note that you need to change the path to the folder where you have the Excel file

```{r}
data_peat<-read_excel("data/edited/Modelling_SDM_species_data.xlsx",
                      sheet="SDM Data")
```

## Have a look at the data

This shows the first rows of your data file in "tibble" format. You can also see the variable type for each variable (double or character).

```{r}
data_peat
```

## Convert some variables to factors

It is better to convert some variables (those that are Y/N or 0/1) to factors.

```{r}
data_peat<-data_peat%>%
  mutate(fen=as.factor(fen),imp_temp=as.factor(imp_temp),
         nutrient=as.factor(nutrient),fire=as.factor(fire),dry=as.factor(dry)) 
# with mutate you create new variables that are equal to the old variables
# but are coded as factors
```

## Convert moist to numeric

For some reason, moist appears as a character variable. It should be numeric, so we convert it.

```{r}
data_peat<-data_peat%>%
  mutate(moist=as.numeric(moist))
```

# Abundance models (zero-inflated beta regressions)

Showing only models without interactions, and with temperature (as used in the main text)

## Plant groups

Abundance of Medium and Fuscum includes 0 and 100 - change 100 to 99.

```{r}
data_peat$Medium<-ifelse(data_peat$Medium>99,99,data_peat$Medium)
data_peat$Fuscum<-ifelse(data_peat$Fuscum>99,99,data_peat$Fuscum)
```

Convert variables to proportions (from 0 to 1) instead of percentages:

```{r}
data_peat<-data_peat%>%
  mutate(tot_Sphagnum_prop=tot_Sphagnum/100,
         Erio_prop=Erio/100,
         Erica_prop=Erica/100,
         Carex_prop=Carex/100,
         Medium_prop=Medium/100,
         Fuscum_prop=Fuscum/100,
         Rubellum_prop=Rubellum/100,
         Balticum_prop=Balticum/100,
         Cuspidata_prop=Cuspidata/100)
```

### Models

```{r}
mod_abund_tot_Sphagnum_temp<-glmmTMB(tot_Sphagnum_prop~temp+moist+nutrient+
                                  fire+dry,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi_temp<-glmmTMB(Erio_prop~temp+moist+nutrient+
                               fire+dry,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi_temp<-glmmTMB(Erica_prop~temp+moist+nutrient+
                                fire+dry,family="beta_family", 
                              ziformula=~0, data=subset(data_peat,Erica_prop>0))
mod_abund_Carex_nozi_temp<-glmmTMB(Carex_prop~temp+moist+nutrient+
                                fire+dry,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

### R2

For the zero-inflated models, you can use the function "r2_zeroinflated", or directly use "r2" for all, as this will return the most appropriate R2 for the given model (i.e. the  R2 for models with zero-inflation component in this case).

For models with no zero inflation, if you use the "r2" function, it returns the Ferrari's R2 (you can also get it using the function "r2_ferrari"). I had never heard about this R2, but there is a reference in the R documentation:
Ferrari, S., and Cribari-Neto, F. (2004). Beta Regression for Modelling Rates and Proportions. Journal of Applied Statistics, 31(7), 799–815. doi:10.1080/0266476042000214501.

Next to each function, I have written as a comment the value that I get. Please check if you get the same value! You mentioned in your email that you got much higher values (around 0.9 or even 1, which are not what I get!). Getting these lower values does not mean that models do not work well, it is quite unusual to get R2 values of 0.9, or even larger than 0.5 I would say, so values of 0.2-0.4, or even lower seem quite OK.

```{r}
r2_zeroinflated(mod_abund_tot_Sphagnum_temp) 
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.374
# adj. R2: 0.337
r2(mod_abund_Erio_nozi_temp) # Ferrari's R2: 0.274
r2(mod_abund_Erica_nozi_temp) #  Ferrari's R2: 0.173
r2(mod_abund_Carex_nozi_temp) #  Ferrari's R2: 0.316
```

## Selected Sphagnum species

### Models

```{r}
mod_abund_Medium_temp<-glmmTMB(Medium_prop~temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_temp<-glmmTMB(Fuscum_prop~temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_temp<-glmmTMB(Rubellum_prop~temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Balticum_temp<-glmmTMB(Balticum_prop~temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Cuspidata_temp<-glmmTMB(Cuspidata_prop~temp+moist+
                               nutrient+fire+dry,family="beta_family",
                             ziformula=~.,data=data_peat) 
```

### R2

```{r}
r2_zeroinflated(mod_abund_Medium_temp)
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.158
# adj. R2: 0.096
r2_zeroinflated(mod_abund_Fuscum_temp)
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.466
# adj. R2: 0.427
r2_zeroinflated(mod_abund_Rubellum_temp)
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.368
# adj. R2: 0.321
r2_zeroinflated(mod_abund_Balticum_temp) 
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.329
# adj. R2: 0.279
r2_zeroinflated(mod_abund_Cuspidata_temp)
# R2 for Zero-Inflated and Hurdle Regression
# R2: 0.047
# adj. R2: -0.024
# Here, I am not sure what a negative value means for the adjusted R-square. 
# After some quick search in Google, it seems that it just might mean that the
# model is a poor fit. See these two links (but maybe worth looking it up a bit more)
# https://stats.stackexchange.com/questions/483582/how-to-interpret-a-negative-adjusted-r-squared
# https://stats.stackexchange.com/questions/34751/is-it-a-problem-to-get-a-negative-adjusted-r-squared
```

# Temporal autocorrelation

## Tests for temporal autocorrelation in residuals

```{r}
library(DHARMa)
```

### Plant groups

```{r}
testTemporalAutocorrelation(simulateResiduals(mod_abund_tot_Sphagnum_temp),
                            subset(data_peat,
                                   !is.na(tot_Sphagnum_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Erio_nozi_temp),
                            subset(data_peat,
                                   Erio_prop>0&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Erica_nozi_temp),
                            subset(data_peat,
                                   Erica_prop>0&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Carex_nozi_temp),
                            subset(data_peat,
                                   Carex_prop>0&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
```

Durbin-Watson test shows significant temporal autocorrelation in all models.

### Selected Sphagnum species

```{r}
testTemporalAutocorrelation(simulateResiduals(mod_abund_Medium_temp),
                            subset(data_peat,
                                   !is.na(Medium_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Fuscum_temp),
                            subset(data_peat,
                                   !is.na(Fuscum_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Rubellum_temp),
                            subset(data_peat,
                                   !is.na(Rubellum_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Balticum_temp),
                            subset(data_peat,
                                   !is.na(Balticum_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
testTemporalAutocorrelation(simulateResiduals(mod_abund_Cuspidata_temp),
                            subset(data_peat,
                                   !is.na(Cuspidata_prop)&!is.na(temp)&
                                     !is.na(moist)&!is.na(nutrient)&
                                     !is.na(fire)&!is.na(dry))$age, plot = T)
```

Durbin-Watson test shows no significant temporal autocorrelation in any of the models.

## AR models for plant groups

Models including an autoregressive covariance structure (AR(1)), see:
https://cran.r-project.org/web/packages/glmmTMB/vignettes/covstruct.html
https://www.flutterbys.com.au/stats/tut/tut8.3a.html

Create daeta with no NAs and times and group variables:

```{r}
data_peat_noNapredictors<-subset(data_peat,!is.na(temp)&!is.na(moist)&
                                   !is.na(nutrient)&!is.na(fire)&!is.na(dry))
times <- factor(data_peat_noNapredictors$age)
group <- factor(rep(1,108))

dat0 <- data.frame(tot_Sphagnum_prop=data_peat_noNapredictors$tot_Sphagnum_prop,
                   Erio_prop=data_peat_noNapredictors$Erio_prop,
                   Erica_prop=data_peat_noNapredictors$Erica_prop,
                   Carex_prop=data_peat_noNapredictors$Carex_prop,
                   temp=data_peat_noNapredictors$temp,
                   age=data_peat_noNapredictors$age,
                   moist=data_peat_noNapredictors$moist,
                   nutrient=data_peat_noNapredictors$nutrient,
                   fire=data_peat_noNapredictors$fire,
                   dry=data_peat_noNapredictors$dry,
                   times, group)

data_peat_noNapredictors_Erica<-subset(data_peat_noNapredictors,Erica_prop>0)
times_Erica <- factor(data_peat_noNapredictors_Erica$age)
group_Erica <- factor(rep(1,107))

dat0_Erica <- data.frame(tot_Sphagnum_prop=subset(data_peat_noNapredictors,
                                                  Erica_prop>0)$tot_Sphagnum_prop,
                   Erio_prop=subset(data_peat_noNapredictors,
                                    Erica_prop>0)$Erio_prop,
                   Erica_prop=subset(data_peat_noNapredictors,
                                     Erica_prop>0)$Erica_prop,
                   Carex_prop=subset(data_peat_noNapredictors,
                                     Erica_prop>0)$Carex_prop,
                   temp=subset(data_peat_noNapredictors,
                               Erica_prop>0)$temp,
                   age=subset(data_peat_noNapredictors,
                              Erica_prop>0)$age,
                   moist=subset(data_peat_noNapredictors,
                                Erica_prop>0)$moist,
                   nutrient=subset(data_peat_noNapredictors,
                                   Erica_prop>0)$nutrient,
                   fire=subset(data_peat_noNapredictors,
                               Erica_prop>0)$fire,
                   dry=subset(data_peat_noNapredictors,
                              Erica_prop>0)$dry,
                   times_Erica, group_Erica)
```

Fit AR models:

```{r}
mod_abund_tot_Sphagnum_temp_AR<-glmmTMB(tot_Sphagnum_prop~temp+moist+nutrient+
                                          fire+dry+ar1(times+0|group),
                                        family="beta_family",
                                        ziformula=~.,
                                        data=data_peat_noNapredictors) 
mod_abund_Erio_nozi_temp_AR<-glmmTMB(Erio_prop~temp+moist+nutrient+
                                       fire+dry+ar1(times+0|group),
                                     family="beta_family",
                                     ziformula=~0,
                                     data=data_peat_noNapredictors,
                                      control=glmmTMBControl(optimizer=optim,
                                                             optArgs=list(method="BFGS")))
mod_abund_Erica_nozi_temp_AR<-glmmTMB(Erica_prop~temp+moist+nutrient+
                                        fire+dry+ar1(times_Erica+0|group_Erica),
                                      family="beta_family", 
                                      ziformula=~0, 
                                      data=dat0_Erica)
mod_abund_Carex_nozi_temp_AR<-glmmTMB(Carex_prop~temp+moist+nutrient+
                                        fire+dry+ar1(times+0|group),
                                      family="beta_family",
                                      ziformula=~0,
                                      data=data_peat_noNapredictors)
```

### Comparing original and AR models

```{r}
summary(mod_abund_tot_Sphagnum_temp)
summary(mod_abund_tot_Sphagnum_temp_AR)
```

```{r}
summary(mod_abund_Erio_nozi_temp)
summary(mod_abund_Erio_nozi_temp_AR)
```

```{r}
summary(mod_abund_Erica_nozi_temp)
summary(mod_abund_Erica_nozi_temp_AR)
```

```{r}
summary(mod_abund_Carex_nozi_temp)
summary(mod_abund_Carex_nozi_temp_AR)
```

# HERE: Ordination

Use partial constrained ordination, where you include time as a covariate that you "partial out" to control for its effect, thus focusing on the variation that is not explained by time:

```{r}
ordination<-capscale(data_ordi2[10:21]~ # species data matrix
                       temp+moist+nutrient+fire+dry+Condition(age), # Environmental variables
                     data = data_ordi2, distance="bray") # Bray-Curtis distance
```

```{r}
vegan::ordiplot(ordination,display = c('species', 'sites', 'bp'))
orditorp(ordination,display="species",cex=0.8,col="red")
```

```{r}
anova (ordination, by = 'margin', permutations = 999)
```

Repeat hierarchical partitioning, etc. 



# Session info

```{r}
sessionInfo()
```

