---
title: Analyses of species distributions in peatlands
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
```

# Load the R packages that you will use

If you do not have the R packages installed, you need to install them. These are the ones that I often use for reading in data, data manipulation, etc. But you can of course use others!

```{r load packages}
library(tidyverse)
library(readxl)
library(knitr)
library(ggeffects)
library(car)
library(glmmTMB)
library(ggthemes)
library(gridExtra)
```

# Data preparation

## Read data from Excel file and convert variables

```{r}
data_peat<-read_excel("data/edited/Modelling_SDM_species_data.xlsx",
                      sheet="SDM Data")
data_peat<-data_peat%>%
  mutate(fen=as.factor(fen),imp_temp=as.factor(imp_temp),
         nutrient=as.factor(nutrient),fire=as.factor(fire),dry=as.factor(dry)) 
# with mutate you create new variables that are equal to the old variables
# but are coded as factors
data_peat<-data_peat%>%
  mutate(moist=as.numeric(moist))
```


# Models for abundance

## Total Sphagnum abundance


```{r}
data_peat<-data_peat%>%
  mutate(tot_Sphagnum_prop=tot_Sphagnum/100)
```

```{r}
mod_abund_tot_Sphagnum<-glmmTMB(tot_Sphagnum_prop~    # Your response variable
                                  age+temp+moist+
                                  nutrient+fire+dry,  # Independent variables
                                family="beta_family", # Use the beta family
                                ziformula=~.,
                                data=data_peat)       # Your data

# ziformula=~. sets the zero-inflation formula identical to the formula
# for the proportion part. This basically means that the same effects will be 
# tested on presence/absence and on abundance.
# If you specify ziformula=~0 this means that there is no zero-inflation, but
# this will throw an error with your data, because you do have zeros.
# You can also specify a different formula for the zero-inflation part,
# for example, ziformula=~age will only test the effect of age
# on presence/absence, but all the effects on abundance
```

```{r}
summary(mod_abund_tot_Sphagnum)
```

```{r}
plot(ggpredict(mod_abund_tot_Sphagnum, 
               # This plots the predicted effect from your model
               type="zi_prob",  # Plots the predicted zero-inflation probability
               terms=c("age[all]")), # For the effect of age 
     add.data=T) # Not adding the data here
```

I am not sure why the error band looks strange on this one (I would need to look into this), but you can see that the effect of age is the opposite as before, because this is the probability of getting a zero.

The effect of nutrient input on the abundance:

```{r}
plot(ggpredict(mod_abund_tot_Sphagnum, 
               # This plots the predicted effect from your model
               type="fixed",  # Plots the predicted effects for the conditional
               # model only (i.e. effects on abundance)
               terms=c("nutrient")), # For the effect of nutrient 
     add.data=TRUE) # You can add the data if you want
```

The effect of dry period on the abundance:

```{r}
plot(ggpredict(mod_abund_tot_Sphagnum, 
               # This plots the predicted effect from your model
               type="fixed",  # Plots the predicted effects for the conditional
               # model only (i.e. effects on abundance)
               terms=c("dry")), # For the effect of dry 
     add.data=FALSE) # I did not add the data here
```

```{r}
plots_sphagnum<-grid.arrange(
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=tot_Sphagnum_prop),
              position = position_jitter(0.1,0.01),size=3,alpha=0.2,shape=16)+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Total Spaghnum abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=tot_Sphagnum_prop),
                position = position_jitter(0.1,0.01),size=3,alpha=0.2,shape=16)+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Total Spaghnum abundance"),
  # age
  # I woulnd't plot this one!
  ggplot()+
    geom_point(data=data_peat,aes(x=age,y=tot_Sphagnum_prop),
               size=3,alpha=0.2,shape=16)+
    geom_ribbon(data=data.frame(ggpredict(mod_abund_tot_Sphagnum,
                                          type="zi_prob",terms=c("age[all]"))),
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                color="grey",alpha=0.3)+
    geom_line(data=data.frame(ggpredict(mod_abund_tot_Sphagnum,
                                        type="zi_prob",terms=c("age[all]"))),
              aes(x=x,y=1-predicted))+
    my_theme()+xlab("Age")+ylab("Probability of total Sphagnum presence"),
  ncol=3
)
ggsave(filename="output/figures/plots_sphagnum.tiff",plot=plots_sphagnum,
       width=36,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_sphagnum.pdf",plot=plots_sphagnum,
       width=36,height=12,units="cm",dpi=300)
```

```{r}
plots_sphagnum_nopoints<-grid.arrange(
  # nutrient
  ggplot()+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Total Spaghnum abundance"),
  # dry
  ggplot()+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Total Spaghnum abundance"),
  ncol=2
)
ggsave(filename="output/figures/plots_sphagnum_nopoints.tiff",
       plot=plots_sphagnum_nopoints,width=24,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_sphagnum_nopoints.pdf",
       plot=plots_sphagnum_nopoints,width=24,height=12,units="cm",dpi=300)
```

## Medium

```{r}
data_peat$Medium<-ifelse(data_peat$Medium>99,99,data_peat$Medium)
data_peat$Fuscum<-ifelse(data_peat$Fuscum>99,99,data_peat$Fuscum)
mod_abund_Medium<-glmmTMB(Medium/100~    # Your response variable
                               age+temp+moist+
                               nutrient+fire+dry,  # Independent variables
                             family="beta_family", # Use the beta family
                             ziformula=~.,         
                             data=data_peat) # Your data

summary(mod_abund_Medium)
```

```{r}
plots_medium<-grid.arrange(
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Medium/100),
              position = position_jitter(0.1,0.01),size=3,alpha=0.2,shape=16)+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Total Medium abundance"),
  # fire
  ggplot()+
    geom_jitter(data=data_peat,aes(x=fire,y=Medium/100),
              position = position_jitter(0.1,0.01),size=3,alpha=0.2,shape=16)+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("fire"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("fire"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Fire")+ylab("Total Medium abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Medium/100),
                position = position_jitter(0.1,0.01),size=3,alpha=0.2,shape=16)+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Total Medium abundance"),
  # age
  ggplot()+
    geom_point(data=data_peat,aes(x=age,y=Medium/100),
               size=3,alpha=0.2,shape=16)+
    geom_ribbon(data=data.frame(ggpredict(mod_abund_Medium,
                                          type="zi_prob",terms=c("age[all]"))),
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                color="grey",alpha=0.3)+
    geom_line(data=data.frame(ggpredict(mod_abund_Medium,
                                        type="zi_prob",terms=c("age[all]"))),
              aes(x=x,y=1-predicted))+
    my_theme()+xlab("Age")+ylab("Probability of Medium presence"),
  ncol=2
)
ggsave(filename="output/figures/plots_medium.tiff",
       plot=plots_medium,width=24,height=24,units="cm",dpi=300)
ggsave(filename="output/figures/plots_medium.pdf",
       plot=plots_medium,width=24,height=24,units="cm",dpi=300)
```


# Session info



```{r}
sessionInfo()
```









