---
title: Analyses of species distributions in peatlands
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
```

# Load the R packages that you will use

If you do not have the R packages installed, you need to install them. 

```{r load packages}
library(tidyverse)
library(readxl)
library(knitr)
library(ggeffects)
library(car)
library(glmmTMB)
library(ggplot2)
library(vegan)
library(rdacca.hp)
library(gridExtra)
library(ggthemes)
library(egg)
library(cowplot)
library(BiodiversityR)
library(ggrepel)
library(performance)
library(sjPlot)
```

# Data preparation

## Read data from Excel file

Note that you need to change the path to the folder where you have the Excel file

```{r}
data_peat<-read_excel("data/edited/Modelling_SDM_species_data.xlsx",
                      sheet="SDM Data")
```

## Have a look at the data

This shows the first rows of your data file in "tibble" format. You can also see the variable type for each variable (double or character).

```{r}
data_peat
```

## Convert some variables to factors

It is better to convert some variables (those that are Y/N or 0/1) to factors.

```{r}
data_peat<-data_peat%>%
  mutate(fen=as.factor(fen),imp_temp=as.factor(imp_temp),
         nutrient=as.factor(nutrient),fire=as.factor(fire),dry=as.factor(dry)) 
# with mutate you create new variables that are equal to the old variables
# but are coded as factors
```

## Convert moist to numeric

For some reason, moist appears as a character variable. It should be numeric, so we convert it.

```{r}
data_peat<-data_peat%>%
  mutate(moist=as.numeric(moist))
```

# Ordinations (vegan package)

Suggested reading: https://www.davidzeleny.net/anadat-r/doku.php/en:ordination

(lots of info on this webpage!)

Chapter 10 in this pdf: https://apps.worldagroforestry.org/downloads/Publications/PDFS/b13695.pdf

Using the vegan package.

I performed some ordinations with Sphagnum species. I tried different methods, but if I would need to choose one, I would do a constrained ordination, specifically a Distance-based redundancy analysis (db-RDA) with Bray-Curtis distance. You can read about all types in the webpage above if you feel like it. 

Data for ordination: 

```{r}
data_ordi2<-data_peat %>%
  filter_at(vars(Balticum:Fallax), 
            all_vars(!is.na(.)))%>% # Remove rows with all NAs
  filter_at(vars(Balticum:Fallax),
            any_vars(.>0))%>% # Remove rows with all zeros - WHY?
  filter(!is.na(age)&!is.na(temp)&!is.na(moist)&!is.na(nutrient)&!is.na(fire)&
           !is.na(dry))%>% # Remove rows with NA in predictors
  rename(Deformed_Acutifolia=`Diseased Acutifolia`) #Rename to avoid problems
```

Distance-based redundancy analysis (db-RDA) with Bray-Curtis distance.

See https://www.davidzeleny.net/anadat-r/doku.php/en:similarity for info on distances.

## APPENDICES: Wtih temperature and age

Calculate ordination:

```{r}
ordi6<-capscale(data_ordi2[10:21]~ # species data matrix
             age+temp+moist+nutrient+fire+dry, # Environmental variables
             data = data_ordi2, distance="bray") # Bray-Curtis distance

```

Result of the ordination:

```{r}
ordi6
```

"Intertia" is the total variance - your environmental variables explain 0.2704 of this variance ("constrained" part).

Proportion explained by each ordination axis. CAP1-CAP6 are the "constrained" axes, explained by your environmental variables. MDS1-MDS34 are the "unconstrained" axes.

```{r}
eigenvals(ordi6) %>%
  summary()
```

Barplot of percentage variance explained by individual axes

```{r}
expl_var_ordi6 <- c(ordi6$CCA$eig/ordi6$tot.chi*100, 
                    ordi6$CA$eig/ordi6$tot.chi*100)
barplot (expl_var_ordi6, col = c(rep ('red', 
                                      length (ordi6$CCA$eig/ordi6$tot.chi*100)), 
                                 rep ('black', 
                                      length (ordi6$CA$eig/ordi6$tot.chi*100))),
         las = 2, ylab = '% variation')
```

Plot of the ordination (species in red and sites-samples in black):

```{r fig.height=6, fig.width=6}
vegan::ordiplot(ordi6,display = c('species', 'sites', 'bp'))
orditorp(ordi6,display="species",cex=0.8,col="red")
```

This shows the two first constrained axes of the ordination. You can see how the sites and species distribute along these axes.

Test significance of the ordination with Monte Carlo permutation test.

For the whole model:

```{r}
anova (ordi6, permutations = 999) 
```

The model is significant.

For each explanatory variable (with all the others used as covariables, independently from their order in the model):

```{r}
anova (ordi6, by = 'margin', permutations = 999)
```

Age, moist, nutrient and dry show significant effects.

For each axis:

```{r}
anova (ordi6, by = 'axis', permutations = 999)
```

Axis 1 and 2 are significant.

Ordination plot with ggplot2.

Install ggord package (you only need to do this once):

```{r}
# Enable the r-universe repo
options(repos = c(
    fawda123 = 'https://fawda123.r-universe.dev',
    CRAN = 'https://cloud.r-project.org'))

# Install ggord
install.packages('ggord')
```

Load ggord package:

```{r}
library(ggord)
```


```{r}
ggord(ordi6,ptslab=T,repel=T,labcol="red",veccol="red",size=NA,addsize=3,
      xlims=c(-1.1,1.1),ylims=c(-1.1,1.1))+
  geom_point(size=3,shape=20,color="black",alpha=0.2)
```

### Hierarchical partitioning

```{r}
dist_matrix<-vegdist(data_ordi2[10:21],method="bray")
```

```{r}
hierpart1<-rdacca.hp(dist_matrix,data_ordi2[c(23:24,26:29)],method = "dbRDA",
          type ="adjR2",scale = F,add = T,sqrt.dist = T)
hierpart1
plot(hierpart1,plot.perc=T)
```

```{r}
cor(data_ordi2[c(23:24)]) # Correlation among age and temp is 0.762
vif.cca(ordi6)
# But VIF of the ordination is not super high, probably ok to keep both
```

## MAIN TEXT: Wtih temperature

Calculate ordination:

```{r}
ordi_temp<-capscale(data_ordi2[10:21]~ # species data matrix
             temp+moist+nutrient+fire+dry, # Environmental variables
             data = data_ordi2, distance="bray") # Bray-Curtis distance
```

Result of the ordination:

```{r}
ordi_temp
```

"Intertia" is the total variance - your environmental variables explain 0.2285 of this variance ("constrained" part).

Proportion explained by each ordination axis. CAP1-CAP5 are the "constrained" axes, explained by your environmental variables. MDS1-MDS34 are the "unconstrained" axes.

```{r}
eigenvals(ordi_temp) %>%
  summary()
```

Barplot of percentage variance explained by individual axes

```{r}
expl_var_ordi_temp <- c(ordi_temp$CCA$eig/ordi_temp$tot.chi*100, 
                    ordi_temp$CA$eig/ordi_temp$tot.chi*100)
barplot (expl_var_ordi_temp, col = c(rep ('red',
                                          length (ordi_temp$CCA$eig/
                                                    ordi_temp$tot.chi*100)),
                                     rep ('black',                                       length(ordi_temp$CA$eig/ordi_temp$tot.chi*100))),
         las = 2, ylab = '% variation')
```

Plot of the ordination (species in red and sites-samples in black):

```{r fig.height=6, fig.width=6}
vegan::ordiplot(ordi_temp,display = c('species', 'sites', 'bp'))
orditorp(ordi_temp,display="species",cex=0.8,col="red")
```

This shows the two first constrained axes of the ordination. You can see how the sites and species distribute along these axes.

Test significance of the ordination with Monte Carlo permutation test.

For the whole model:

```{r}
anova (ordi_temp, permutations = 999) 
```

The model is significant.

For each explanatory variable (with all the others used as covariables, independently from their order in the model):

```{r}
anova (ordi_temp, by = 'margin', permutations = 999)
```

Temp, moist, nutrient and dry show significant effects.

For each axis:

```{r}
anova (ordi_temp, by = 'axis', permutations = 999)
```

Axis 1 and 2 are significant.

Ordination plot with ggplot2.

```{r}
ggord(ordi_temp,ptslab=T,repel=T,labcol="red",veccol="red",size=NA,addsize=3,
      xlims=c(-1.1,1.1),ylims=c(-1.1,1.1))+
  geom_point(size=3,shape=20,color="black",alpha=0.2)
```

### Hierarchical partitioning

```{r}
hierpart_temp<-rdacca.hp(dist_matrix,data_ordi2[c(24,26:29)],method = "dbRDA",
          type ="adjR2",scale = F,add = T,sqrt.dist = T)
hierpart_temp
plot(hierpart_temp,plot.perc=T)
```

```{r}
vif.cca(ordi_temp)
# VIFs of the ordination all below 2
```

## APPENDICES: Wtih age

Calculate ordination:

```{r}
ordi_age<-capscale(data_ordi2[10:21]~ # species data matrix
             age+moist+nutrient+fire+dry, # Environmental variables
             data = data_ordi2, distance="bray") # Bray-Curtis distance
```

Result of the ordination:

```{r}
ordi_age
```

"Intertia" is the total variance - your environmental variables explain 0.2600 of this variance ("constrained" part).

Proportion explained by each ordination axis. CAP1-CAP5 are the "constrained" axes, explained by your environmental variables. MDS1-MDS34 are the "unconstrained" axes.

```{r}
eigenvals(ordi_age) %>%
  summary()
```

Barplot of percentage variance explained by individual axes

```{r}
expl_var_ordi_age <- c(ordi_age$CCA$eig/ordi_age$tot.chi*100, 
                    ordi_age$CA$eig/ordi_age$tot.chi*100)
barplot (expl_var_ordi_age, col = c(rep ('red',
                                          length (ordi_age$CCA$eig/
                                                    ordi_age$tot.chi*100)),
                                     rep ('black',                                       length(ordi_age$CA$eig/ordi_age$tot.chi*100))),
         las = 2, ylab = '% variation')
```

Plot of the ordination (species in red and sites-samples in black):

```{r fig.height=6, fig.width=6}
vegan::ordiplot(ordi_age,display = c('species', 'sites', 'bp'))
orditorp(ordi_age,display="species",cex=0.8,col="red")
```

This shows the two first constrained axes of the ordination. You can see how the sites and species distribute along these axes.

Test significance of the ordination with Monte Carlo permutation test.

For the whole model:

```{r}
anova (ordi_age, permutations = 999) 
```

The model is significant.

For each explanatory variable (with all the others used as covariables, independently from their order in the model):

```{r}
anova (ordi_age, by = 'margin', permutations = 999)
```

Age, moist, nutrient and dry show significant effects.

For each axis:

```{r}
anova (ordi_age, by = 'axis', permutations = 999)
```

Axis 1 and 2 are significant.

Ordination plot with ggplot2.

```{r}
ggord(ordi_age,ptslab=T,repel=T,labcol="red",veccol="red",size=NA,addsize=3,
      xlims=c(-1.1,1.1),ylims=c(-1.1,1.1))+
  geom_point(size=3,shape=20,color="black",alpha=0.2)
```

### Hierarchical partitioning

```{r}
hierpart_age<-rdacca.hp(dist_matrix,data_ordi2[c(23,26:29)],method = "dbRDA",
          type ="adjR2",scale = F,add = T,sqrt.dist = T)
hierpart_age
plot(hierpart_age,plot.perc=T)
```

```{r}
vif.cca(ordi_age)
# VIFs of the ordination all below 2
```

# Abundance models (zero-inflated beta regressions)

## Without interactions

Check how many rows with each species absent:

```{r}
nrow(data_peat%>%filter(tot_Sphagnum==0))
nrow(data_peat%>%filter(Erio==0)) # 1 row
nrow(data_peat%>%filter(Carex==0)) # 2 rows
nrow(data_peat%>%filter(Erica==0)) # 5 rows
nrow(data_peat%>%filter(Balticum==0))
nrow(data_peat%>%filter(Medium==0))
nrow(data_peat%>%filter(Cuspidata==0))
nrow(data_peat%>%filter(Austinii==0))
nrow(data_peat%>%filter(Fuscum==0))
nrow(data_peat%>%filter(Rubellum==0))
# More species?
```

Erio, Erica and Carex have too few rows with absences. Presence/absence models will not work for these species. Fit models oinly for the abundance of those species.

Abundance of Medium and Fuscum includes 0 and 100 - change 100 to 99.

```{r}
data_peat$Medium<-ifelse(data_peat$Medium>99,99,data_peat$Medium)
data_peat$Fuscum<-ifelse(data_peat$Fuscum>99,99,data_peat$Fuscum)
```

Convert variables to proportions (from 0 to 1) instead of percentages:

```{r}
data_peat<-data_peat%>%
  mutate(tot_Sphagnum_prop=tot_Sphagnum/100,
         Erio_prop=Erio/100,
         Erica_prop=Erica/100,
         Carex_prop=Carex/100,
         Medium_prop=Medium/100,
         Fuscum_prop=Fuscum/100,
         Rubellum_prop=Rubellum/100,
         Balticum_prop=Balticum/100,
         Cuspidata_prop=Cuspidata/100)
```

Check combinations of the three factors and the fen-bog factor:

```{r}
with(data_peat,table(fen,nutrient))
with(data_peat,table(fen,fire))
with(data_peat,table(fen,dry))
```

There are 0 cases where fen=Y and nutrient=1 so we will not be able to test the fen*nutrient interactions. We can include all interactions but this one in the models.

### Plant groups

#### APPENDICES: age and temp

```{r}
mod_abund_tot_Sphagnum<-glmmTMB(tot_Sphagnum_prop~age+temp+moist+nutrient+
                                  fire+dry,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi<-glmmTMB(Erio_prop~age+temp+moist+nutrient+
                               fire+dry,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi<-glmmTMB(Erica_prop~age+temp+moist+nutrient+
                                fire+dry,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
mod_abund_Carex_nozi<-glmmTMB(Carex_prop~age+temp+moist+nutrient+
                                fire+dry,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

```{r}
summary(mod_abund_tot_Sphagnum)
summary(mod_abund_Erio_nozi)
summary(mod_abund_Erica_nozi)
summary(mod_abund_Carex_nozi)
```

##### Plots Total Sphagnum

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plots_sphagnum<-grid.arrange(
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=tot_Sphagnum_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Total Sphagnum abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=tot_Sphagnum_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Total Sphagnum abundance"),
  ncol=2
)
ggsave(filename="output/figures/plots_sphagnum.tiff",plot=plots_sphagnum,
       width=24,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_sphagnum.pdf",plot=plots_sphagnum,
       width=24,height=12,units="cm",dpi=300)
```

##### Plots Erio

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plots_Erio<-grid.arrange(
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Erio_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Erio abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Erio_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Erio abundance"),
  ncol=2
)
ggsave(filename="output/figures/plots_Erio.tiff",plot=plots_Erio,
       width=24,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Erio.pdf",plot=plots_Erio,
       width=24,height=12,units="cm",dpi=300)
```

##### Plots Erica

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plots_Erica<-ggplot()+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_Erica_nozi,
                                        type="fixed",terms=c("temp[all]"))),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_Erica_nozi,
                                      type="fixed",terms=c("temp[all]"))),
            aes(x=x,y=predicted))+
  geom_point(data=subset(data_peat,Erica_prop>0),aes(x=temp,y=Erica_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Erica abundance")
ggsave(filename="output/figures/plots_Erica.tiff",plot=plots_Erica,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Erica.pdf",plot=plots_Erica,
       width=12,height=12,units="cm",dpi=300)
```

##### Plots Carex

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plots_Carex<-grid.arrange(
  # temp
  ggplot()+
    geom_ribbon(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                          type="fixed",terms=c("temp[all]"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                alpha=0.2)+
    geom_line(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                        type="fixed",terms=c("temp[all]"))),
              aes(x=x,y=predicted))+
    geom_point(data=subset(data_peat,Carex_prop>0),aes(x=temp,y=Carex_prop),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Temperature")+ylab("Carex abundance"),
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Carex_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Carex abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Carex_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Carex abundance"),
  ncol=3
)
ggsave(filename="output/figures/plots_Carex.tiff",plot=plots_Carex,
       width=36,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Carex.pdf",plot=plots_Carex,
       width=36,height=12,units="cm",dpi=300)
```

#### Selected Sphagnum species

```{r}
mod_abund_Medium<-glmmTMB(Medium_prop~age+temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum<-glmmTMB(Fuscum_prop~age+temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum<-glmmTMB(Rubellum_prop~age+temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Balticum<-glmmTMB(Balticum_prop~age+temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Cuspidata<-glmmTMB(Cuspidata_prop~age+temp+moist+
                               nutrient+fire+dry,family="beta_family",
                             ziformula=~.,data=data_peat) 
```

```{r}
summary(mod_abund_Medium)
summary(mod_abund_Fuscum)
summary(mod_abund_Rubellum)
summary(mod_abund_Balticum)
summary(mod_abund_Cuspidata)
```

##### Plots Medium

Using ggemmeans with type="zi_prob" gives error "Error: This prediction-type is currently not available for models of class 'glmmTMB'".

So for age, I am using ggpredict and calculating an average prediction

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Medium_age<-rbind(
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Medium,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
plots_Medium<-grid.arrange(
  # age
  ggplot()+
    geom_ribbon(data=average_prediction_Medium_age,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                alpha=0.2)+
    geom_line(data=average_prediction_Medium_age,
              aes(x=x,y=1-predicted))+
    geom_point(data=data_peat,aes(x=age,y=Medium_prop),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Age")+ylab("Probability of Medium presence"),
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Medium_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("nutrient"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("nutrient"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient input")+ylab("Medium abundance"),
  # fire
  ggplot()+
    geom_jitter(data=data_peat,aes(x=fire,y=Medium_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("fire"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("fire"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Fire")+ylab("Medium abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Medium_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Medium,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Medium abundance"),
  ncol=2
)
ggsave(filename="output/figures/plots_Medium.tiff",plot=plots_Medium,
       width=24,height=24,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Medium.pdf",plot=plots_Medium,
       width=24,height=24,units="cm",dpi=300)
```

##### Plots Fuscum

Create average predictions for the effects of moisture and nutrients on the zero-inflated part.

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Fuscum_moist<-rbind(
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%  # NaNs produced
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Fuscum_nutrient<-rbind(
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Fuscum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
plots_Fuscum<-grid.arrange(
  # moist - CI band looking a bit weird
  ggplot()+
    geom_ribbon(data=average_prediction_Fuscum_moist,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                alpha=0.2)+
    geom_line(data=average_prediction_Fuscum_moist,
              aes(x=x,y=1-predicted))+
    geom_point(data=data_peat,aes(x=moist,y=Fuscum_prop),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Moisture")+ylab("Probability of Fuscum presence"),
  # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Fuscum_prop),
                position=position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=average_prediction_Fuscum_nutrient,
               aes(x=x,y=1-predicted),size=4,shape=16)+
    geom_errorbar(data=average_prediction_Fuscum_nutrient,
               aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
               width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient")+ylab("Probability of Fuscum presence"),
  # age
  ggplot()+
    geom_ribbon(data=data.frame(ggemmeans(mod_abund_Fuscum,
                                          type="fixed",terms=c("age"))),
                                aes(x=x,y=predicted,
                                    ymin=conf.low,ymax=conf.high),alpha=0.2)+
    geom_line(data=data.frame(ggemmeans(mod_abund_Fuscum,
                                          type="fixed",terms=c("age"))),
                              aes(x=x,y=predicted))+
    geom_point(data=data_peat,aes(x=age,y=Fuscum_prop),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Age")+ylab("Fuscum abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Fuscum_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Fuscum,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Fuscum,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Fuscum abundance"),
  ncol=2
)
ggsave(filename="output/figures/plots_Fuscum.tiff",plot=plots_Fuscum,
       width=24,height=24,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Fuscum.pdf",plot=plots_Fuscum,
       width=24,height=24,units="cm",dpi=300)
```

##### Plots Rubellum
 
Create average predictions for the effects of nutrients and dry on the zero-inflated part.

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Rubellum_nutrient<-rbind(
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
``` 
 
```{r}
# Create average line among factors=0 and factors=1
average_prediction_Rubellum_dry<-rbind(
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("dry"),
                   condition=c(fire=1,nutrient=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("dry"),
                   condition=c(fire=0,nutrient=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("dry"),
                   condition=c(fire=0,nutrient=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Rubellum,type="zi_prob",terms=c("dry"),
                   condition=c(fire=1,nutrient=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
``` 
 
```{r}
plots_Rubellum<-grid.arrange(
    # nutrient
  ggplot()+
    geom_jitter(data=data_peat,aes(x=nutrient,y=Rubellum_prop),
                position=position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=average_prediction_Rubellum_nutrient,
               aes(x=x,y=1-predicted),size=4,shape=16)+
    geom_errorbar(data=average_prediction_Rubellum_nutrient,
               aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
               width=0.2,size=0.5)+
    my_theme()+xlab("Nutrient")+ylab("Probability of Rubellum presence"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Rubellum_prop),
                position=position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=average_prediction_Rubellum_dry,
               aes(x=x,y=1-predicted),size=4,shape=16)+
    geom_errorbar(data=average_prediction_Rubellum_dry,
               aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
               width=0.2,size=0.5)+
    my_theme()+xlab("Dry")+ylab("Probability of Rubellum presence"),
  # fire
  ggplot()+
    geom_jitter(data=data_peat,aes(x=fire,y=Rubellum_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Rubellum,
                                         type="fixed",terms=c("fire"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Rubellum,
                                            type="fixed",terms=c("fire"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("fire")+ylab("Rubellum abundance"),
  ncol=3
)
ggsave(filename="output/figures/plots_Rubellum.tiff",plot=plots_Rubellum,
       width=36,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Rubellum.pdf",plot=plots_Rubellum,
       width=36,height=12,units="cm",dpi=300)
```

##### Plots Balticum

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Balticum_age<-rbind(
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Balticum,type="zi_prob",terms=c("age[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
plots_Balticum<-grid.arrange(
  # age
  ggplot()+
    geom_ribbon(data=average_prediction_Balticum_age,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                alpha=0.2)+
    geom_line(data=average_prediction_Balticum_age,
              aes(x=x,y=1-predicted))+
    geom_point(data=data_peat,aes(x=age,y=Balticum_prop),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Age")+ylab("Probability of Balticum presence"),
  # moist
  ggplot()+
    geom_ribbon(data=data.frame(ggemmeans(mod_abund_Balticum,
                                          type="fixed",terms=c("moist[all]"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
    geom_line(data=data.frame(ggemmeans(mod_abund_Balticum,
                                        type="fixed",terms=c("moist[all]"))),
              aes(x=x,y=predicted))+
    geom_point(data=data_peat,aes(x=moist,y=Balticum_prop),
               size=3,alpha=0.3,shape=16,color="darkturquoise")+
    my_theme()+xlab("Moisture")+ylab("Balticum abundance"),
  # dry
  ggplot()+
    geom_jitter(data=data_peat,aes(x=dry,y=Balticum_prop),
                position = position_jitter(0.1,0.01),
                size=3,alpha=0.3,shape=16,color="darkturquoise")+
    geom_point(data=data.frame(ggemmeans(mod_abund_Balticum,
                                         type="fixed",terms=c("dry"))),
               aes(x=x,y=predicted),size=4,shape=16)+
    geom_errorbar(data=data.frame(ggemmeans(mod_abund_Balticum,
                                            type="fixed",terms=c("dry"))),
                  aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                  width=0.2,size=0.5)+
    my_theme()+xlab("Dry period")+ylab("Balticum abundance"),
  ncol=3
)
ggsave(filename="output/figures/plots_Balticum.tiff",plot=plots_Balticum,
       width=36,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plots_Balticum.pdf",plot=plots_Balticum,
       width=36,height=12,units="cm",dpi=300)
```

#### Check VIFs of all models

```{r}
plot(check_collinearity(mod_abund_tot_Sphagnum))
plot(check_collinearity(mod_abund_Erio_nozi))
plot(check_collinearity(mod_abund_Erica_nozi))
plot(check_collinearity(mod_abund_Carex_nozi))
plot(check_collinearity(mod_abund_Medium))
plot(check_collinearity(mod_abund_Fuscum))
plot(check_collinearity(mod_abund_Rubellum))
plot(check_collinearity(mod_abund_Balticum))
plot(check_collinearity(mod_abund_Cuspidata))
```

Age and temp always over 2.

#### Tables Appendices

```{r}
tab_model(mod_abund_tot_Sphagnum,mod_abund_Erio_nozi,
          mod_abund_Erica_nozi,mod_abund_Carex_nozi,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("Total Sphagnum","Eriophorum","Erica","Carex"))
```

```{r}
tab_model(mod_abund_Medium,mod_abund_Fuscum,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. medium","S. fuscum"))
```

```{r}
tab_model(mod_abund_Rubellum,mod_abund_Balticum,
          mod_abund_Cuspidata,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. rubellum","S. balticum","S. cuspidata"))
```

### MAIN TEXT: temperature

#### Plant groups

```{r}
mod_abund_tot_Sphagnum_temp<-glmmTMB(tot_Sphagnum_prop~temp+moist+nutrient+
                                  fire+dry,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi_temp<-glmmTMB(Erio_prop~temp+moist+nutrient+
                               fire+dry,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi_temp<-glmmTMB(Erica_prop~temp+moist+nutrient+
                                fire+dry,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
mod_abund_Carex_nozi_temp<-glmmTMB(Carex_prop~temp+moist+nutrient+
                                fire+dry,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

```{r}
plot(check_collinearity(mod_abund_tot_Sphagnum_temp))
plot(check_collinearity(mod_abund_Erio_nozi_temp))
plot(check_collinearity(mod_abund_Erica_nozi_temp))
plot(check_collinearity(mod_abund_Carex_nozi_temp))
```

VIFs are all under 2 now

```{r}
summary(mod_abund_tot_Sphagnum_temp)
summary(mod_abund_Erio_nozi_temp)
summary(mod_abund_Erica_nozi_temp)
summary(mod_abund_Carex_nozi_temp)
```

CHANGES from previous models:

Total Sphagnum: significant effect of temp in the model with only temp (both in the conditional and zero-inflation parts of the model). Significant effect of nutrient in the zero-inflation part in the mdoel with only temp. All previously significant effects stay. 

Erio: significant effect of temp in the model with only temp.

Erica: No changes (temp still significant in the model with only temp)

Carex: No changes.

##### Table 1

```{r}
tab_model(mod_abund_tot_Sphagnum_temp,mod_abund_Erio_nozi_temp,
          mod_abund_Erica_nozi_temp,mod_abund_Carex_nozi_temp,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("Total Sphagnum","Eriophorum","Erica","Carex"))
```

#### Selected Sphagnum species

```{r}
mod_abund_Medium_temp<-glmmTMB(Medium_prop~temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_temp<-glmmTMB(Fuscum_prop~temp+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_temp<-glmmTMB(Rubellum_prop~temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Balticum_temp<-glmmTMB(Balticum_prop~temp+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Cuspidata_temp<-glmmTMB(Cuspidata_prop~temp+moist+
                               nutrient+fire+dry,family="beta_family",
                             ziformula=~.,data=data_peat) 
```

```{r}
plot(check_collinearity(mod_abund_Medium_temp))
# All under 2
plot(check_collinearity(mod_abund_Fuscum_temp))
# All under 2
plot(check_collinearity(mod_abund_Rubellum_temp))
# Fire just over 2 in the conditional component
plot(check_collinearity(mod_abund_Balticum_temp))
# All but temp over 2 in the conditional component
plot(check_collinearity(mod_abund_Cuspidata_temp))
# Dry, moist and nutrient over 2 in the conditional component
```

```{r}
summary(mod_abund_Medium_temp)
summary(mod_abund_Fuscum_temp)
summary(mod_abund_Rubellum_temp)
summary(mod_abund_Balticum_temp)
summary(mod_abund_Cuspidata_temp)
```

##### Table 2

```{r}
tab_model(mod_abund_Medium_temp,mod_abund_Fuscum_temp,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. medium","S. fuscum"))
```

##### Table 3

```{r}
tab_model(mod_abund_Rubellum_temp,mod_abund_Balticum_temp,
          mod_abund_Cuspidata_temp,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. rubellum","S. balticum","S. cuspidata"))
```

##### Rubellum, Balticum and Cuspidata: models with single variables in the condtiional part

```{r}
mod_abund_Rubellum_temponly<-glmmTMB(Rubellum_prop~temp,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_temponly<-glmmTMB(Balticum_prop~temp,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_temponly<-glmmTMB(Cuspidata_prop~temp,family="beta_family",
                             ziformula=~.,
                             data=data_peat)
mod_abund_Rubellum_moistonly<-glmmTMB(Rubellum_prop~moist,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_moistonly<-glmmTMB(Balticum_prop~moist,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_moistonly<-glmmTMB(Cuspidata_prop~moist,family="beta_family",
                             ziformula=~.,
                             data=data_peat)
mod_abund_Rubellum_nutrientonly<-glmmTMB(Rubellum_prop~nutrient,
                                         family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_nutrientonly<-glmmTMB(Balticum_prop~nutrient,
                                         family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_nutrientonly<-glmmTMB(Cuspidata_prop~nutrient,
                                          family="beta_family",
                             ziformula=~.,
                             data=data_peat)
mod_abund_Rubellum_fireonly<-glmmTMB(Rubellum_prop~fire,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_fireonly<-glmmTMB(Balticum_prop~fire,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_fireonly<-glmmTMB(Cuspidata_prop~fire,family="beta_family",
                             ziformula=~.,
                             data=data_peat)
mod_abund_Rubellum_dryonly<-glmmTMB(Rubellum_prop~dry,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_dryonly<-glmmTMB(Balticum_prop~dry,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_dryonly<-glmmTMB(Cuspidata_prop~dry,family="beta_family",
                             ziformula=~.,
                             data=data_peat)
```

These results should be added to Table 3:

```{r}
summary(mod_abund_Rubellum_temponly)
summary(mod_abund_Balticum_temponly)
summary(mod_abund_Cuspidata_temponly)
summary(mod_abund_Rubellum_moistonly)
summary(mod_abund_Balticum_moistonly)
summary(mod_abund_Cuspidata_moistonly)
summary(mod_abund_Rubellum_nutrientonly)
summary(mod_abund_Balticum_nutrientonly)
summary(mod_abund_Cuspidata_nutrientonly)
summary(mod_abund_Rubellum_fireonly)
summary(mod_abund_Balticum_fireonly)
summary(mod_abund_Cuspidata_fireonly)
summary(mod_abund_Rubellum_dryonly)
summary(mod_abund_Balticum_dryonly)
summary(mod_abund_Cuspidata_dryonly)
```

### APPENDICES: age

#### Plant groups

```{r}
mod_abund_tot_Sphagnum_age<-glmmTMB(tot_Sphagnum_prop~age+moist+nutrient+
                                  fire+dry,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi_age<-glmmTMB(Erio_prop~age+moist+nutrient+
                               fire+dry,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi_age<-glmmTMB(Erica_prop~age+moist+nutrient+
                                fire+dry,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
mod_abund_Carex_nozi_age<-glmmTMB(Carex_prop~age+moist+nutrient+
                                fire+dry,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

```{r}
plot(check_collinearity(mod_abund_tot_Sphagnum_age))
plot(check_collinearity(mod_abund_Erio_nozi_age))
plot(check_collinearity(mod_abund_Erica_nozi_age))
plot(check_collinearity(mod_abund_Carex_nozi_age))
```

All under 2.

```{r}
summary(mod_abund_tot_Sphagnum_age)
summary(mod_abund_Erio_nozi_age)
summary(mod_abund_Erica_nozi_age)
summary(mod_abund_Carex_nozi_age)
```

#### Selected Sphagnum species

```{r}
mod_abund_Medium_age<-glmmTMB(Medium_prop~age+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_age<-glmmTMB(Fuscum_prop~age+moist+
                            nutrient+fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_age<-glmmTMB(Rubellum_prop~age+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Balticum_age<-glmmTMB(Balticum_prop~age+moist+
                              nutrient+fire+dry,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Cuspidata_age<-glmmTMB(Cuspidata_prop~age+moist+
                               nutrient+fire+dry,family="beta_family",
                             ziformula=~.,data=data_peat)
```

```{r}
plot(check_collinearity(mod_abund_Medium_age))
# All under 2
plot(check_collinearity(mod_abund_Fuscum_age))
# All under 2
plot(check_collinearity(mod_abund_Rubellum_age))
# Fire just over 2 in the conditional component
plot(check_collinearity(mod_abund_Balticum_age))
# All over 2 in the conditional component
plot(check_collinearity(mod_abund_Cuspidata_age))
# Dry, moist and nutrient over 2 in the conditional component
```

##### Rubellum, Balticum and Cuspidata: models with single variables in the condtiional part

```{r}
mod_abund_Rubellum_ageonly<-glmmTMB(Rubellum_prop~age,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Balticum_ageonly<-glmmTMB(Balticum_prop~age,family="beta_family",
                            ziformula=~.,
                            data=data_peat) 
mod_abund_Cuspidata_ageonly<-glmmTMB(Cuspidata_prop~age,family="beta_family",
                             ziformula=~.,
                             data=data_peat)
# For other predictors, see below
```

```{r}
summary(mod_abund_Rubellum_ageonly)
summary(mod_abund_Balticum_ageonly)
summary(mod_abund_Cuspidata_ageonly)
```

#### Tables Appendices

```{r}
tab_model(mod_abund_tot_Sphagnum_age,mod_abund_Erio_nozi_age,
          mod_abund_Erica_nozi_age,mod_abund_Carex_nozi_age,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("Total Sphagnum","Eriophorum","Erica","Carex"))
```

```{r}
tab_model(mod_abund_Medium_age,mod_abund_Fuscum_age,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. medium","S. fuscum"))
```

```{r}
tab_model(mod_abund_Rubellum_age,mod_abund_Balticum_age,
          mod_abund_Cuspidata_age,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("S. rubellum","S. balticum","S. cuspidata"))
```

## With fen-bog and interactions

### MAIN TEXT: temperature 

Plant groups only

#### Step 1: Models with all interactions (except fen*nutrient)

In these models I include all interactions of fen with the other variables (except for fen*nutrient which will give problems).

```{r}
mod_abund_tot_Sphagnum_temp_all_ints<-glmmTMB(tot_Sphagnum_prop~(temp+moist+
                                  fire+dry)*fen+nutrient,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi_temp_all_ints<-glmmTMB(Erio_prop~(temp+moist+
                               fire+dry)*fen+nutrient,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi_temp_all_ints<-glmmTMB(Erica_prop~(temp+moist+
                                fire+dry)*fen+nutrient,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
mod_abund_Carex_nozi_temp_all_ints<-glmmTMB(Carex_prop~(temp+moist+
                                fire+dry)*fen+nutrient,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

```{r}
summary(mod_abund_tot_Sphagnum_temp_all_ints)
summary(mod_abund_Erio_nozi_temp_all_ints)
summary(mod_abund_Erica_nozi_temp_all_ints)
summary(mod_abund_Carex_nozi_temp_all_ints)
```

#### Step 2: Models with only significant interactions

In these models I include only the interactions of fen with the other variables that were significant in step 1. If one interaction was significant only in the abundance part ("conditional model") or on the presence part ("zero-inflation model") I inlcude it only on that part of the model. 

```{r}
# Total Sphagnum: significant interaction fire*fen 
# included ONLY in the zero-inflated part
mod_abund_tot_Sphagnum_temp_sig_ints<-glmmTMB(tot_Sphagnum_prop~temp+moist+
                                  nutrient+dry+fire+fen,family="beta_family",
                                ziformula=~temp+moist+
                                  nutrient+dry+fire+fen+fire:fen,data=data_peat) 
# Erio: significant interaction temp*fen
mod_abund_Erio_nozi_temp_sig_ints<-glmmTMB(Erio_prop~temp*fen+moist+
                               fire+dry+nutrient,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
# Not anymore significant!
# Erica: significant interaction fire*fen and dry*fen
mod_abund_Erica_nozi_temp_sig_ints<-glmmTMB(Erica_prop~temp+moist+fire+dry+
                                              nutrient+fen+fen:fire+fen:dry,
                                            family="beta_family",                               ziformula=~0,subset(data_peat,Erica_prop>0))
# dry:fen Not anymore significant!
# Carex: no significant interactions
```

```{r}
summary(mod_abund_tot_Sphagnum_temp_sig_ints)
summary(mod_abund_Erio_nozi_temp_sig_ints)
summary(mod_abund_Erica_nozi_temp_sig_ints)
```

###### Table 4

```{r}
tab_model(mod_abund_tot_Sphagnum_temp_sig_ints,
          mod_abund_Erio_nozi_temp_sig_ints,mod_abund_Erica_nozi_temp_sig_ints,
          show.ci=F,show.se=T,show.stat=T,digits=3,show.intercept=F,
          show.r2=F,show.obs=F,transform=NULL,
          dv.labels=c("Total Sphagnum","Eriophorum","Erica"))
```

###### Plots interactions Total Sphagnum

Using ggemmeans with type="zi_prob" gives error "Error: This prediction-type is currently not available for models of class 'glmmTMB'".

So for fire, I am using ggpredict and calculating an average prediction

Create average prediction for the effects of fire:fen on the zero-inflated part:

```{r}
average_prediction_total_Sphagnum_fire_fen<-rbind(
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=1,dry=1)))%>%
    rename(fire=group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=0,dry=0)))%>%
    rename(fire=group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=0,dry=1)))%>%
    rename(fire=group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=1,dry=0)))%>%
    rename(fire=group)%>%mutate(type="d")
  )%>%
  group_by(x,fire)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
plot_sphagnum_int<-ggplot()+
  geom_jitter(data=data_peat,aes(x=fen,y=tot_Sphagnum_prop,color=fire),
              position=position_jitterdodge(jitter.width=0.1,
                                            jitter.height=0.01,
                                            dodge.width=0.5),
              size=3,alpha=0.2,shape=16)+
  geom_point(data=average_prediction_total_Sphagnum_fire_fen,
             aes(x=x,y=1-predicted,color=fire),
             size=4,shape=16,position=position_dodge(0.5))+
  geom_errorbar(data=average_prediction_total_Sphagnum_fire_fen,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high,
                    color=fire),
                width=0.2,size=0.5,position=position_dodge(0.5))+
  scale_color_manual(values=c("#fdae61","#d7191c"))+
  my_theme()+xlab("Fen")+ylab("Probability of total Sphagnum presence")
plot_sphagnum_int
ggsave(filename="output/figures/plot_sphagnum_int.tiff",plot=plot_sphagnum_int,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plot_sphagnum_int.pdf",plot=plot_sphagnum_int,
       width=12,height=12,units="cm",dpi=300)
```

##### Plots interactions Erio

```{r}
plot_Erio_int<-ggplot()+
  geom_point(data=data_peat,aes(x=temp,y=Erio_prop,color=fen),
             size=3,alpha=0.2,shape=16)+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp_sig_ints,
                                          type="fixed",terms=c("temp","fen"))),
                              aes(x=x,y=predicted,fill=group,
                                  ymin=conf.low,ymax=conf.high),
              alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp_sig_ints,
                                          type="fixed",terms=c("temp","fen"))),
                              aes(x=x,y=predicted,color=group))+
  my_theme()+xlab("Temperature")+ylab("Erio abundance")+
  scale_color_manual(values=c("#CC6699","#339966"))+
  scale_fill_manual(values=c("#CC6699","#339966"))
plot_Erio_int
ggsave(filename="output/figures/plot_Erio_int.tiff",plot=plot_Erio_int,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plot_Erio_int.pdf",plot=plot_Erio_int,
       width=12,height=12,units="cm",dpi=300)
```


###### Plots interactions Erica

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plot_Erica_int<-ggplot()+
  geom_jitter(data=data_peat,aes(x=fen,y=Erica_prop,color=fire),
              position=position_jitterdodge(jitter.width=0.1,
                                            jitter.height=0.01,
                                            dodge.width=0.5),
              size=3,alpha=0.2,shape=16)+
  geom_point(data=data.frame(ggemmeans(mod_abund_Erica_nozi_temp_sig_ints,
                                        type="fixed",terms=c("fen","fire"))),
              aes(x=x,y=predicted,color=group),
             size=4,shape=16,position=position_dodge(0.5))+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erica_nozi_temp_sig_ints,
                                      type="fixed",terms=c("fen","fire"))),
            aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,color=group),
            width=0.2,size=0.5,position=position_dodge(0.5))+
  scale_color_manual(values=c("#fdae61","#d7191c"))+
  my_theme()+xlab("Fen")+ylab("Erica abundance")
plot_Erica_int
ggsave(filename="output/figures/plot_Erica_int.tiff",plot=plot_Erica_int,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plot_Erica_int.pdf",plot=plot_Erica_int,
       width=12,height=12,units="cm",dpi=300)
```

```{r}
plot(ggemmeans(mod_abund_Erica_nozi_temp_sig_ints,terms=c("fen","fire")))
```

### (NOT NEEDED?): age and temp

#### Plant groups

##### Step 1: Models with all interactions (except fen*nutrient)

In these models I include all interactions of fen with the other variables (except for fen*nutrient which will give problems).

```{r}
mod_abund_tot_Sphagnum_all_ints<-glmmTMB(tot_Sphagnum_prop~(age+temp+moist+
                                  fire+dry)*fen+nutrient,family="beta_family",
                                ziformula=~.,data=data_peat) 
mod_abund_Erio_nozi_all_ints<-glmmTMB(Erio_prop~(age+temp+moist+
                               fire+dry)*fen+nutrient,family="beta_family",
                             ziformula=~0,data=subset(data_peat,Erio_prop>0))
mod_abund_Erica_nozi_all_ints<-glmmTMB(Erica_prop~(age+temp+moist+
                                fire+dry)*fen+nutrient,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
mod_abund_Carex_nozi_all_ints<-glmmTMB(Carex_prop~(age+temp+moist+
                                fire+dry)*fen+nutrient,family="beta_family",
                              ziformula=~0,data=subset(data_peat,Carex_prop>0))
```

```{r}
summary(mod_abund_tot_Sphagnum_all_ints)
summary(mod_abund_Erio_nozi_all_ints)
summary(mod_abund_Erica_nozi_all_ints)
summary(mod_abund_Carex_nozi_all_ints)
```

##### Step 2: Models with only significant interactions

In these models I include only the interactions of fen with the other variables that were significant in step 1. If one interaction was significant only in the abundance part ("conditional model") or on the presence part ("zero-inflation model") I inlcude it only on that part of the model. 

```{r}
# Total Sphagnum: significant interaction fire*fen 
# included ONLY in the zero-inflated part
mod_abund_tot_Sphagnum_sig_ints<-glmmTMB(tot_Sphagnum_prop~age+temp+moist+
                                  nutrient+dry+fire+fen,family="beta_family",
                                ziformula=~age+temp+moist+
                                  nutrient+dry+fire+fen+fire:fen,data=data_peat) 
# Erio: no significant interactions
# Erica: significant interaction fire*fen 
mod_abund_Erica_nozi_sig_ints<-glmmTMB(Erica_prop~age+temp+moist+
                                fire*fen+dry+nutrient,family="beta_family", 
                              ziformula=~0, data_erica<-subset(data_peat,Erica>0))
# Carex: no significant interactions
```

```{r}
summary(mod_abund_tot_Sphagnum_sig_ints)
summary(mod_abund_Erica_nozi_sig_ints)
```

###### Plots interactions Total Sphagnum

Using ggemmeans with type="zi_prob" gives error "Error: This prediction-type is currently not available for models of class 'glmmTMB'".

So for fire, I am using ggpredict and calculating an average prediction

Create average prediction for the effects of fire:fen on the zero-inflated part:

```{r}
average_prediction_total_Sphagnum_fire_fen<-rbind(
  tibble(ggpredict(mod_abund_tot_Sphagnum_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=1,dry=1)))%>%
    rename(fire=group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=0,dry=0)))%>%
    rename(fire=group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=0,dry=1)))%>%
    rename(fire=group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_sig_ints,type="zi_prob",
                   terms=c("fen","fire"),
                   condition=c(nutrient=1,dry=0)))%>%
    rename(fire=group)%>%mutate(type="d")
  )%>%
  group_by(x,fire)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
plot_sphagnum_int<-ggplot()+
  geom_jitter(data=data_peat,aes(x=fen,y=tot_Sphagnum_prop,color=fire),
              position=position_jitterdodge(jitter.width=0.1,
                                            jitter.height=0.01,
                                            dodge.width=0.5),
              size=3,alpha=0.2,shape=16)+
  geom_point(data=average_prediction_total_Sphagnum_fire_fen,
             aes(x=x,y=1-predicted,color=fire),
             size=4,shape=16,position=position_dodge(0.5))+
  geom_errorbar(data=average_prediction_total_Sphagnum_fire_fen,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high,
                    color=fire),
                width=0.2,size=0.5,position=position_dodge(0.5))+
  scale_color_manual(values=c("#fdae61","#d7191c"))+
  my_theme()+xlab("Fen")+ylab("Probability of total Sphagnum presence")
plot_sphagnum_int
ggsave(filename="output/figures/plot_sphagnum_int.tiff",plot=plot_sphagnum_int,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plot_sphagnum_int.pdf",plot=plot_sphagnum_int,
       width=12,height=12,units="cm",dpi=300)
```

###### Plots interactions Erica

Using ggemmeans: averages over the proportions of the categories of factors.

```{r}
plot_Erica_int<-ggplot()+
  geom_jitter(data=data_peat,aes(x=fen,y=Erica_prop,color=fire),
              position=position_jitterdodge(jitter.width=0.1,
                                            jitter.height=0.01,
                                            dodge.width=0.5),
              size=3,alpha=0.2,shape=16)+
  geom_point(data=data.frame(ggemmeans(mod_abund_Erica_nozi_sig_ints,
                                        type="fixed",terms=c("fen","fire"))),
              aes(x=x,y=predicted,color=group),
             size=4,shape=16,position=position_dodge(0.5))+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erica_nozi_sig_ints,
                                      type="fixed",terms=c("fen","fire"))),
            aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,color=group),
            width=0.2,size=0.5,position=position_dodge(0.5))+
  scale_color_manual(values=c("#fdae61","#d7191c"))+
  my_theme()+xlab("Fen")+ylab("Erica abundance")
plot_Erica_int
ggsave(filename="output/figures/plot_Erica_int.tiff",plot=plot_Erica_int,
       width=12,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/plot_Erica_int.pdf",plot=plot_Erica_int,
       width=12,height=12,units="cm",dpi=300)
```

```{r}
plot(ggemmeans(mod_abund_Erica_nozi_sig_ints,terms=c("fen","fire")))
```

#### Selected Sphagnum species

##### Step 1: Models with all interactions (except fen*nutrient)

For these models, we will use the subset of data_peat where total proportion of Sphagnum is > 0, and moist is not NA.

```{r}
nrow(subset(data_peat,tot_Sphagnum_prop>0&!is.na(moist)))
```

These are 88 rows of data_peat.

Check combinations of the three factors and the fen-bog factor in this subset:

```{r}
with(subset(data_peat,tot_Sphagnum_prop>0&!is.na(moist)),table(fen,nutrient))
with(subset(data_peat,tot_Sphagnum_prop>0&!is.na(moist)),table(fen,fire))
with(subset(data_peat,tot_Sphagnum_prop>0&!is.na(moist)),table(fen,dry))
```

Interaction with nutrient should give problems as before, but I do not see why the others should give problems.

In these models I include all interactions of fen with the other variables (except for fen*nutrient which will give problems).

```{r}
mod_abund_Medium_all_ints<-glmmTMB(Medium_prop~(age+temp+moist+
                            fire+dry)*fen+nutrient,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_all_ints<-glmmTMB(Fuscum_prop~(age+temp+moist+
                            fire+dry)*fen+nutrient,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_all_ints<-glmmTMB(Rubellum_prop~(age+temp+moist+
                            fire+dry)*fen+nutrient,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Balticum_all_ints<-glmmTMB(Balticum_prop~(age+temp+moist+
                            fire+dry)*fen+nutrient,family="beta_family",
                            ziformula=~.,data=data_peat) 
mod_abund_Cuspidata_all_ints<-glmmTMB(Cuspidata_prop~(age+temp+moist+
                            fire+dry)*fen+nutrient,family="beta_family",
                             ziformula=~.,data=data_peat) 
```

I get these warnings for each model:
Warning messages:
1: In fitTMB(TMBStruc) :
  Model convergence problem; non-positive-definite Hessian matrix. See vignette('troubleshooting')
2: In fitTMB(TMBStruc) :
  Model convergence problem; singular convergence (7). See vignette('troubleshooting')
  
```{r}
summary(mod_abund_Medium_all_ints)
summary(mod_abund_Fuscum_all_ints)
summary(mod_abund_Rubellum_all_ints)
summary(mod_abund_Balticum_all_ints)
summary(mod_abund_Cuspidata_all_ints)
```
  
And all the NaNs in the summaries.

I looked here https://cran.r-project.org/web/packages/glmmTMB/vignettes/troubleshooting.html but I am not sure how to solve this. It might be that the model is overparameterized (i.e. the data does not contain enough information to estimate the parameters reliably). So maybe here you should try to test the interactions one by one. Although then you do it in a different way for the plant groups and for the selected Sphagnum species. But I cannot think of a better solution!

##### Step 1 (alternative): Models testing interactions one by one (except fen*nutrient)

Try to test each interaction separately (except with nutrient):

```{r}
mod_abund_Medium_age_int<-glmmTMB(Medium_prop~age*fen+temp+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Medium_temp_int<-glmmTMB(Medium_prop~age+temp*fen+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Medium_moist_int<-glmmTMB(Medium_prop~age+temp+moist*fen+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Medium_fire_int<-glmmTMB(Medium_prop~age+temp+moist+nutrient+
                            fire*fen+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Medium_dry_int<-glmmTMB(Medium_prop~age+temp+moist+nutrient+
                            fire+dry*fen,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_age_int<-glmmTMB(Fuscum_prop~age*fen+temp+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_temp_int<-glmmTMB(Fuscum_prop~age+temp*fen+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_moist_int<-glmmTMB(Fuscum_prop~age+temp+moist*fen+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_fire_int<-glmmTMB(Fuscum_prop~age+temp+moist+nutrient+
                            fire*fen+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Fuscum_dry_int<-glmmTMB(Fuscum_prop~age+temp+moist+nutrient+
                            fire+dry*fen,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_age_int<-glmmTMB(Rubellum_prop~age*fen+temp+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_temp_int<-glmmTMB(Rubellum_prop~age+temp*fen+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_moist_int<-glmmTMB(Rubellum_prop~age+temp+moist*fen+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_fire_int<-glmmTMB(Rubellum_prop~age+temp+moist+nutrient+
                            fire*fen+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Rubellum_dry_int<-glmmTMB(Rubellum_prop~age+temp+moist+nutrient+
                            fire+dry*fen,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Balticum_age_int<-glmmTMB(Balticum_prop~age*fen+temp+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Balticum_temp_int<-glmmTMB(Balticum_prop~age+temp*fen+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Balticum_moist_int<-glmmTMB(Balticum_prop~age+temp+moist*fen+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Balticum_fire_int<-glmmTMB(Balticum_prop~age+temp+moist+nutrient+
                            fire*fen+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Balticum_dry_int<-glmmTMB(Balticum_prop~age+temp+moist+nutrient+
                            fire+dry*fen,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Cuspidata_age_int<-glmmTMB(Cuspidata_prop~age*fen+temp+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Cuspidata_temp_int<-glmmTMB(Cuspidata_prop~age+temp*fen+moist+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Cuspidata_moist_int<-glmmTMB(Cuspidata_prop~age+temp+moist*fen+nutrient+
                            fire+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Cuspidata_fire_int<-glmmTMB(Cuspidata_prop~age+temp+moist+nutrient+
                            fire*fen+dry,family="beta_family",
                          ziformula=~.,data=data_peat)
mod_abund_Cuspidata_dry_int<-glmmTMB(Cuspidata_prop~age+temp+moist+nutrient+
                            fire+dry*fen,family="beta_family",
                          ziformula=~.,data=data_peat)
```

```{r}
summary(mod_abund_Medium_age_int) # Model OK, interaction NS
summary(mod_abund_Medium_temp_int) # Model OK, interaction NS
summary(mod_abund_Medium_moist_int) # Model OK, interaction NS
summary(mod_abund_Medium_fire_int) # Model OK, interaction NS
summary(mod_abund_Medium_dry_int) # Model OK, interaction NS
summary(mod_abund_Fuscum_age_int) # NaNs produced
summary(mod_abund_Fuscum_temp_int) # NaNs produced
summary(mod_abund_Fuscum_moist_int) # NaNs produced
summary(mod_abund_Fuscum_fire_int) # NaNs produced
summary(mod_abund_Fuscum_dry_int) # NaNs produced
summary(mod_abund_Rubellum_age_int) # NaNs produced
summary(mod_abund_Rubellum_temp_int) # NaNs produced
summary(mod_abund_Rubellum_moist_int) # NaNs produced
summary(mod_abund_Rubellum_fire_int) # NaNs produced
summary(mod_abund_Rubellum_dry_int) # NaNs produced
summary(mod_abund_Balticum_age_int) # NaNs produced
summary(mod_abund_Balticum_temp_int) # NaNs produced
summary(mod_abund_Balticum_moist_int) # NaNs produced
summary(mod_abund_Balticum_fire_int) # NaNs produced
summary(mod_abund_Balticum_dry_int) # NaNs produced
summary(mod_abund_Cuspidata_age_int) # NaNs produced
summary(mod_abund_Cuspidata_temp_int) # NaNs produced
summary(mod_abund_Cuspidata_moist_int) # NaNs produced
summary(mod_abund_Cuspidata_fire_int) # NaNs produced
summary(mod_abund_Cuspidata_dry_int) # NaNs produced
```

I am not sure why the models for Medium work OK, but not the models for the other species. I guess it might also be a problem of sample size - maybe there is not enough data to estimate so many parameters in the model. These models have 88 observations, while the moddels for the plant groups have 108 observations, and this might make a difference (although still not sure why it worked in the case of Medium). Anyway, I think it might be better to only test the interactions for the plant groups (i.e. total Sphagnum, Erio, Erica, Carex),but not for the Sphagnum species. You can say in the text that you did not test the interactions for Sphagnum species because of the reduced sample size. 

# Combined plots

## Figure 1: Ordination

Check: 
https://rstudio-pubs-static.s3.amazonaws.com/694016_e2d53d65858d4a1985616fa3855d237f.html

### APPENDICES: Wtih temperature and age

Ordination plot with vegan:

```{r}
ordination_plot<-ordiplot(ordi6,display = c('species', 'sites', 'bp'))
```

Extract information on the locations of sites (circles in the ordiplot) via function sites.long. Information on characteristics of the sites is added via the argument of env.data.

Extract information on species with function species.long.

```{r}
sites.long1 <- sites.long(ordination_plot, env.data=data_ordi2)
species.long2 <- species.long(ordination_plot)
row.names(species.long2)<-c("Balticum","Medium","Cuspidata","Austinii","Fuscum",
                            "Rubellum","Acutifolia","Deformed Acutifolia",
                            "Angustifolium","Tenellum","Papillosum","Fallax" )
head(sites.long1)
species.long2
```

```{r}
vectors.long3  <- data.frame(summary(ordi6)$biplot[,1:2])
row.names(vectors.long3)<-c("Age","Temperature","Moisture","Nutrient input = 1",
                            "Fire = 1","Dry period = 1")
```

```{r}
figure1app1_a <- ggplot() + 
  geom_vline(xintercept = c(0), color = "grey70", linetype = 2) +
  geom_hline(yintercept = c(0), color = "grey70", linetype = 2) +
  xlab("Axis 1 (14.1%)") + ylab("Axis 2 (6.4%)") +  coord_fixed()+
  scale_x_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +
  scale_y_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +  
  geom_point(data=sites.long1,aes(x=axis1, y=axis2),
             size=3,alpha=0.3,shape=16,color="darkturquoise") + 
  geom_point(data=species.long2,aes(x=axis1, y=axis2),
             size=2,shape=1,color="brown2") +
  geom_text_repel(data=species.long2,aes(x=axis1, y=axis2, label=labels),
                  colour="brown2",size=3,family="serif")+
  geom_segment(data=vectors.long3, aes(x=0, y=0, xend=CAP1*2, yend=CAP2*2), 
               color="black", size=0.5,arrow=arrow(length=unit(0.02,"npc"))) +
  geom_text_repel(data=vectors.long3[1,],
                  aes(x=CAP1*2.15,y=CAP2*2.05,
                      label=rownames(vectors.long3[1,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  geom_text_repel(data=vectors.long3[2,],
                  aes(x=CAP1*2.4,y=CAP2*2.3,
                      label=rownames(vectors.long3[2,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  geom_text_repel(data=vectors.long3[3,],
                  aes(x=CAP1*2.5,y=CAP2*2.3,
                      label=rownames(vectors.long3[3,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  geom_text_repel(data=vectors.long3[4,],
                  aes(x=CAP1*2.4,y=CAP2*2.2,
                      label=rownames(vectors.long3[4,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  geom_text_repel(data=vectors.long3[5,],
                  aes(x=CAP1*3.5,y=CAP2*2.5,
                      label=rownames(vectors.long3[5,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  geom_text_repel(data=vectors.long3[6,],
                  aes(x=CAP1*7,y=CAP2*3.5,
                      label=rownames(vectors.long3[6,])), 
            cex=3,direction="both",segment.size=0.25,color="black",
            family="serif") +
  my_theme()
figure1app1_b<-ggplot(data.frame(hierpart1$Hier.part)%>%
         rownames_to_column(var="variable")%>%
         mutate(variable=c("Age","Temperature","Moisture",
                           "Nutrient input","Fire","Dry period"))%>%
         mutate(variable=factor(variable,
                                levels=c("Age","Temperature","Moisture",
                                         "Nutrient input","Fire","Dry period"))),
       aes(x=variable,y=I.perc...))+geom_bar(stat = "identity")+
  my_theme()+xlab(NULL)+ylab("Individual effect to R square (%)")
figure1app1<-cowplot::plot_grid(figure1app1_a,figure1app1_b,ncol=2,labels=c("A)","B)"),
                   label_fontfamily="serif",align="hv")
figure1app1  
ggsave(filename="output/figures/figure1app1.tiff",plot=figure1app1,
       width=30,height=14,units="cm",dpi=300)
ggsave(filename="output/figures/figure1app1.pdf",plot=figure1app1,
       width=30,height=14,units="cm",dpi=300)
```

### MAIN TEXT: With temperature

Ordination plot with vegan:

```{r}
ordination_plot_temp<-ordiplot(ordi_temp,display = c('species', 'sites', 'bp'))
```

Extract information on the locations of sites (circles in the ordiplot) via function sites.long. Information on characteristics of the sites is added via the argument of env.data.

Extract information on species with function species.long.

```{r}
sites.long1_temp <- sites.long(ordination_plot_temp, env.data=data_ordi2)
species.long2_temp <- species.long(ordination_plot_temp)
row.names(species.long2_temp)<-c("Balticum","Medium","Cuspidata","Austinii",
                                 "Fuscum","Rubellum","Acutifolia",
                                 "Deformed Acutifolia","Angustifolium",
                                 "Tenellum","Papillosum","Fallax" )
head(sites.long1_temp)
species.long2_temp
```

```{r}
vectors.long3_temp  <- data.frame(summary(ordi_temp)$biplot[,1:2])
row.names(vectors.long3_temp)<-c("Temperature","Moisture","Nutrient input = 1",
                            "Fire = 1","Dry period = 1")
```

```{r}
figure1_a <- ggplot() + 
  geom_vline(xintercept = c(0), color = "grey70", linetype = 2) +
  geom_hline(yintercept = c(0), color = "grey70", linetype = 2) +
  xlab("Axis 1 (11.4%)") + ylab("Axis 2 (6.0%)") +  coord_fixed()+
  scale_x_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +
  scale_y_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +  
  geom_point(data=sites.long1_temp,aes(x=axis1, y=axis2),
             size=3,alpha=0.3,shape=16,color="darkturquoise") + 
  geom_point(data=species.long2_temp,aes(x=axis1, y=axis2),
             size=2,shape=1,color="brown2") +
  geom_text_repel(data=species.long2_temp,aes(x=axis1, y=axis2, label=labels),
                  colour="brown2",size=3,family="serif")+
  geom_segment(data=vectors.long3_temp, aes(x=0, y=0, xend=CAP1*2, yend=CAP2*2), 
               color="black", size=0.5,arrow=arrow(length=unit(0.02,"npc"))) +
  geom_text_repel(data=vectors.long3_temp[1,],
                  aes(x=CAP1*2.16,y=CAP2*2.4,
                      label=rownames(vectors.long3_temp[1,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_temp[2,],
                  aes(x=CAP1*2.3,y=CAP2*2.3,
                      label=rownames(vectors.long3_temp[2,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_temp[3,],
                  aes(x=CAP1*2.5,y=CAP2*2.3,
                      label=rownames(vectors.long3_temp[3,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_temp[4,],
                  aes(x=CAP1*2.7,y=CAP2*2.2,
                      label=rownames(vectors.long3_temp[4,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_temp[5,],
                  aes(x=CAP1*4.5,y=CAP2*2.5,
                      label=rownames(vectors.long3_temp[5,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  my_theme()
figure1_b<-ggplot(data.frame(hierpart_temp$Hier.part)%>%
         rownames_to_column(var="variable")%>%
         mutate(variable=c("Temperature","Moisture",
                           "Nutrient input","Fire","Dry period"))%>%
         mutate(variable=factor(variable,
                                levels=c("Temperature","Moisture",
                                         "Nutrient input","Fire","Dry period"))),
       aes(x=variable,y=I.perc...))+geom_bar(stat = "identity")+
  my_theme()+xlab(NULL)+ylab("Individual effect to R square (%)")
figure1<-cowplot::plot_grid(figure1_a,figure1_b,ncol=2,labels=c("A)","B)"),
                   label_fontfamily="serif",align="hv")
figure1  
ggsave(filename="output/figures/figure1.tiff",plot=figure1,
       width=30,height=14,units="cm",dpi=300)
ggsave(filename="output/figures/figure1.pdf",plot=figure1,
       width=30,height=14,units="cm",dpi=300)
```

### APPENDICES: With age

Ordination plot with vegan:

```{r}
ordination_plot_age<-ordiplot(ordi_age,display = c('species', 'sites', 'bp'))
```

Extract information on the locations of sites (circles in the ordiplot) via function sites.long. Information on characteristics of the sites is added via the argument of env.data.

Extract information on species with function species.long.

```{r}
sites.long1_age <- sites.long(ordination_plot_age, env.data=data_ordi2)
species.long2_age <- species.long(ordination_plot_age)
row.names(species.long2_age)<-c("Balticum","Medium","Cuspidata","Austinii",
                                 "Fuscum","Rubellum","Acutifolia",
                                 "Deformed Acutifolia","Angustifolium",
                                 "Tenellum","Papillosum","Fallax" )
head(sites.long1_age)
species.long2_age
```

```{r}
vectors.long3_age  <- data.frame(summary(ordi_age)$biplot[,1:2])
row.names(vectors.long3_age)<-c("Age","Moisture","Nutrient input = 1",
                            "Fire = 1","Dry period = 1")
```

```{r}
figure1app2_a <- ggplot() + 
  geom_vline(xintercept = c(0), color = "grey70", linetype = 2) +
  geom_hline(yintercept = c(0), color = "grey70", linetype = 2) +
  xlab("Axis 1 (14.0%)") + ylab("Axis 2 (6.4%)") +  coord_fixed()+
  scale_x_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +
  scale_y_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +  
  geom_point(data=sites.long1_age,aes(x=axis1, y=axis2),
             size=3,alpha=0.3,shape=16,color="darkturquoise") + 
  geom_point(data=species.long2_age,aes(x=axis1, y=axis2),
             size=2,shape=1,color="brown2") +
  geom_text_repel(data=species.long2_age,aes(x=axis1, y=axis2, label=labels),
                  colour="brown2",size=3,family="serif")+
  geom_segment(data=vectors.long3_age, aes(x=0, y=0, xend=CAP1*2, yend=CAP2*2), 
               color="black", size=0.5,arrow=arrow(length=unit(0.02,"npc"))) +
  geom_text_repel(data=vectors.long3_age[1,],
                  aes(x=CAP1*2.16,y=CAP2*2.4,
                      label=rownames(vectors.long3_age[1,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_age[2,],
                  aes(x=CAP1*2.3,y=CAP2*2.3,
                      label=rownames(vectors.long3_age[2,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_age[3,],
                  aes(x=CAP1*2.5,y=CAP2*2.3,
                      label=rownames(vectors.long3_age[3,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_age[4,],
                  aes(x=CAP1*2.7,y=CAP2*2.2,
                      label=rownames(vectors.long3_age[4,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  geom_text_repel(data=vectors.long3_age[5,],
                  aes(x=CAP1*4.5,y=CAP2*2.5,
                      label=rownames(vectors.long3_age[5,])), 
                  cex=3,direction="both",segment.size=0.25,color="black",
                  family="serif") +
  my_theme()
figure1app2_b<-ggplot(data.frame(hierpart_age$Hier.part)%>%
         rownames_to_column(var="variable")%>%
         mutate(variable=c("Age","Moisture",
                           "Nutrient input","Fire","Dry period"))%>%
         mutate(variable=factor(variable,
                                levels=c("Age","Moisture",
                                         "Nutrient input","Fire","Dry period"))),
       aes(x=variable,y=I.perc...))+geom_bar(stat = "identity")+
  my_theme()+xlab(NULL)+ylab("Individual effect to R square (%)")
figure1app2<-cowplot::plot_grid(figure1app2_a,figure1app2_b,ncol=2,labels=c("A)","B)"),
                   label_fontfamily="serif",align="hv")
figure1app2  
ggsave(filename="output/figures/figure1app2.tiff",plot=figure1app2,
       width=30,height=14,units="cm",dpi=300)
ggsave(filename="output/figures/figure1app2.pdf",plot=figure1app2,
       width=30,height=14,units="cm",dpi=300)
```

<!-- ## OLD: Figure 2: Plant groups -->

<!-- ```{r} -->
<!-- figure2_a_1<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=nutrient,y=tot_Sphagnum_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum, -->
<!--                                            type="fixed",terms=c("nutrient"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum, -->
<!--                                               type="fixed",terms=c("nutrient"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--   scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8,1))+ -->
<!--   my_theme()+xlab("Nutrient input")+ylab("Total Sphagnum abundance") + -->
<!--       theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure2_a_2<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=dry,y=tot_Sphagnum_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum, -->
<!--                                            type="fixed",terms=c("dry"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum, -->
<!--                                               type="fixed",terms=c("dry"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--   scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8,1))+ -->
<!--       my_theme()+xlab("Dry period")+ylab("Total Sphagnum abundance") +  -->
<!--       theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure2_b_1<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=nutrient,y=Erio_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi, -->
<!--                                            type="fixed",terms=c("nutrient"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi, -->
<!--                                               type="fixed",terms=c("nutrient"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--   scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+ -->
<!--       my_theme()+xlab("Nutrient input")+ylab("Erio abundance")+ -->
<!--       theme(plot.margin = margin(l=10,r = 5,t=10,b=10)) -->
<!-- figure2_b_2<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=dry,y=Erio_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi, -->
<!--                                            type="fixed",terms=c("dry"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi, -->
<!--                                               type="fixed",terms=c("dry"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--   scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+ -->
<!--       my_theme()+xlab("Dry period")+ylab("Erio abundance")+ -->
<!--       theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure2d_1<-ggplot()+ -->
<!--       geom_ribbon(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                             type="fixed",terms=c("temp[all]"))), -->
<!--                   aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                   alpha=0.2)+ -->
<!--       geom_line(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                           type="fixed",terms=c("temp[all]"))), -->
<!--                 aes(x=x,y=predicted))+ -->
<!--       geom_point(data=subset(data_peat,Carex_prop>0),aes(x=temp,y=Carex_prop), -->
<!--                  size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       my_theme()+xlab("Temperature")+ylab("Carex abundance")+ -->
<!--       theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure2_d_2<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=nutrient,y=Carex_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                            type="fixed",terms=c("nutrient"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                               type="fixed",terms=c("nutrient"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--       my_theme()+xlab("Nutrient input")+ylab("Carex abundance")+ -->
<!--       theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(l=5,r = 5,t=10,b=10)) -->
<!-- figure2_d_3<-ggplot()+ -->
<!--       geom_jitter(data=data_peat,aes(x=dry,y=Carex_prop), -->
<!--                   position = position_jitter(0.1,0.01), -->
<!--                   size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--       geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                            type="fixed",terms=c("dry"))), -->
<!--                  aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--       geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi, -->
<!--                                               type="fixed",terms=c("dry"))), -->
<!--                     aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                     width=0.2,size=0.5)+ -->
<!--       my_theme()+xlab("Dry period")+ylab("Carex abundance")+ -->
<!--       theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- figure2_a<-ggarrange(# Total Sphagnum -->
<!--       figure2_a_1,figure2_a_2,nrow=1) -->
<!-- figure2_b<-ggarrange(# Erio -->
<!--       figure2_b_1,figure2_b_2,nrow = 1) -->
<!-- figure2_c<-ggarrange(# Erica -->
<!--       plots_Erica+theme(plot.margin=margin(l = 5,t=10,b=10)),nrow = 1) -->
<!-- figure2_d<-ggarrange(# Carex -->
<!--       figure2d_1,figure2_d_2,figure2_d_3,nrow = 1) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- figure2<-cowplot::plot_grid( -->
<!--   cowplot::plot_grid(figure2_a,figure2_b,ncol=2,labels=c("A)","B)"), -->
<!--             label_fontfamily="serif")+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   cowplot::plot_grid(figure2_c,figure2_d,ncol=2,labels=c("C)","D)"), -->
<!--             label_fontfamily="serif",rel_widths=c(0.27,0.73))+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   nrow=2) -->
<!-- figure2 -->
<!-- ggsave(filename="output/figures/figure2.tiff",plot=figure2, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ggsave(filename="output/figures/figure2.pdf",plot=figure2, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ``` -->

<!-- ## OLD: Figure 3: Selected Sphagnum species: Fuscum and Rubellum -->

<!-- ```{r} -->
<!-- figure3_a_1<-ggplot()+ -->
<!--     geom_ribbon(data=average_prediction_Fuscum_moist, -->
<!--                 aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                 alpha=0.2)+ -->
<!--     geom_line(data=average_prediction_Fuscum_moist, -->
<!--               aes(x=x,y=1-predicted))+ -->
<!--     geom_point(data=data_peat,aes(x=moist,y=Fuscum_prop), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     my_theme()+xlab("Moisture")+ylab("Probability of Fuscum presence")+ -->
<!--   theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure3_a_2<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=nutrient,y=Fuscum_prop), -->
<!--                 position=position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=average_prediction_Fuscum_nutrient, -->
<!--                aes(x=x,y=1-predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=average_prediction_Fuscum_nutrient, -->
<!--                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Nutrient")+ylab("Probability of Fuscum presence")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure3_b_1<-ggplot()+ -->
<!--     geom_ribbon(data=data.frame(ggemmeans(mod_abund_Fuscum, -->
<!--                                           type="fixed",terms=c("age"))), -->
<!--                                 aes(x=x,y=predicted, -->
<!--                                     ymin=conf.low,ymax=conf.high),alpha=0.2)+ -->
<!--     geom_line(data=data.frame(ggemmeans(mod_abund_Fuscum, -->
<!--                                           type="fixed",terms=c("age"))), -->
<!--                               aes(x=x,y=predicted))+ -->
<!--     geom_point(data=data_peat,aes(x=age,y=Fuscum_prop), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     my_theme()+xlab("Age")+ylab("Fuscum abundance")+ -->
<!--   theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure3_b_2<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=dry,y=Fuscum_prop), -->
<!--                 position = position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=data.frame(ggemmeans(mod_abund_Fuscum, -->
<!--                                          type="fixed",terms=c("dry"))), -->
<!--                aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=data.frame(ggemmeans(mod_abund_Fuscum, -->
<!--                                             type="fixed",terms=c("dry"))), -->
<!--                   aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                   width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Dry period")+ylab("Fuscum abundance")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure3_c_1<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=nutrient,y=Rubellum_prop), -->
<!--                 position=position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=average_prediction_Rubellum_nutrient, -->
<!--                aes(x=x,y=1-predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=average_prediction_Rubellum_nutrient, -->
<!--                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Nutrient")+ylab("Probability of Rubellum presence")+ -->
<!--   theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure3_c_2<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=dry,y=Rubellum_prop), -->
<!--                 position=position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=average_prediction_Rubellum_dry, -->
<!--                aes(x=x,y=1-predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=average_prediction_Rubellum_dry, -->
<!--                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Dry period")+ylab("Probability of Rubellum presence")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure3_d<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=fire,y=Rubellum_prop), -->
<!--                 position = position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=data.frame(ggemmeans(mod_abund_Rubellum, -->
<!--                                          type="fixed",terms=c("fire"))), -->
<!--                aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=data.frame(ggemmeans(mod_abund_Rubellum, -->
<!--                                             type="fixed",terms=c("fire"))), -->
<!--                   aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                   width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Fire")+ylab("Rubellum abundance")+ -->
<!--   theme(plot.margin=margin(r = 10,l = 5,t=10,b=10)) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- figure3_a<-ggarrange(figure3_a_1,figure3_a_2,nrow=1) -->
<!-- figure3_b<-ggarrange(figure3_b_1,figure3_b_2,nrow=1) -->
<!-- figure3_c<-ggarrange(figure3_c_1,figure3_c_2,nrow=1) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- figure3<-cowplot::plot_grid( -->
<!--   cowplot::plot_grid(figure3_a,figure3_b,ncol=2,labels=c("A)","B)"), -->
<!--             label_fontfamily="serif")+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   cowplot::plot_grid(figure3_c,figure3_d,ncol=2,labels=c("C)","D)"), -->
<!--             label_fontfamily="serif",rel_widths=c(0.64,0.36))+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   nrow=2) -->
<!-- figure3 -->
<!-- ggsave(filename="output/figures/figure3.tiff",plot=figure3, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ggsave(filename="output/figures/figure3.pdf",plot=figure3, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ``` -->

<!-- ## OLD: Figure 4: Selected Sphagnum species: Medium and Balticum -->

<!-- ```{r} -->
<!-- figure4_a<-ggarrange( -->
<!--   ggplot()+ -->
<!--     geom_ribbon(data=average_prediction_Medium_age, -->
<!--                 aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                 alpha=0.2)+ -->
<!--     geom_line(data=average_prediction_Medium_age, -->
<!--               aes(x=x,y=1-predicted))+ -->
<!--     geom_point(data=data_peat,aes(x=age,y=Medium_prop), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     my_theme()+xlab("Age")+ylab("Probability of Medium presence")+ -->
<!--     theme(plot.margin=margin(l = 5,t=10,b=10)),nrow = 1) -->
<!-- figure4_b_1<-ggplot()+ -->
<!--   geom_jitter(data=data_peat,aes(x=nutrient,y=Medium_prop), -->
<!--               position = position_jitter(0.1,0.01), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--   geom_point(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                          type="fixed",terms=c("nutrient"))), -->
<!--              aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--   geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                           type="fixed",terms=c("nutrient"))), -->
<!--                 aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                 width=0.2,size=0.5)+ -->
<!--   my_theme()+xlab("Nutrient input")+ylab("Medium abundance")+ -->
<!--   theme(plot.margin = margin(l=10,r = 5,t=10,b=10)) -->
<!-- figure4_b_2<-ggplot()+ -->
<!--   geom_jitter(data=data_peat,aes(x=fire,y=Medium_prop), -->
<!--               position = position_jitter(0.1,0.01), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--   geom_point(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                        type="fixed",terms=c("fire"))), -->
<!--              aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--   geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                           type="fixed",terms=c("fire"))), -->
<!--                 aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                 width=0.2,size=0.5)+ -->
<!--   my_theme()+xlab("Fire")+ylab("Medium abundance")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--         axis.title.y = element_blank(), -->
<!--         plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure4_b_3<-ggplot()+ -->
<!--   geom_jitter(data=data_peat,aes(x=dry,y=Medium_prop), -->
<!--               position = position_jitter(0.1,0.01), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--   geom_point(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                        type="fixed",terms=c("dry"))), -->
<!--              aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--   geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium, -->
<!--                                           type="fixed",terms=c("dry"))), -->
<!--                 aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                 width=0.2,size=0.5)+ -->
<!--   my_theme()+xlab("Dry period")+ylab("Medium abundance")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--         axis.title.y = element_blank(), -->
<!--         plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- figure4_c<-ggplot()+ -->
<!--     geom_ribbon(data=average_prediction_Balticum_age, -->
<!--                 aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high), -->
<!--                 alpha=0.2)+ -->
<!--     geom_line(data=average_prediction_Balticum_age, -->
<!--               aes(x=x,y=1-predicted))+ -->
<!--     geom_point(data=data_peat,aes(x=age,y=Balticum_prop), -->
<!--               size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     my_theme()+xlab("Age")+ylab("Probability of Balticum presence")+ -->
<!--   theme(plot.margin=margin(l = 5,t=10,b=10)) -->
<!-- figure4_d_1<-ggplot()+ -->
<!--     geom_ribbon(data=data.frame(ggemmeans(mod_abund_Balticum, -->
<!--                                           type="fixed",terms=c("moist[all]"))), -->
<!--                 aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+ -->
<!--     geom_line(data=data.frame(ggemmeans(mod_abund_Balticum, -->
<!--                                         type="fixed",terms=c("moist[all]"))), -->
<!--               aes(x=x,y=predicted))+ -->
<!--     geom_point(data=data_peat,aes(x=moist,y=Balticum_prop), -->
<!--                size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     my_theme()+xlab("Moisture")+ylab("Balticum abundance")+ -->
<!--   theme(plot.margin = margin(l=10,r = 5,t=10,b=10) ) -->
<!-- figure4_d_2<-ggplot()+ -->
<!--     geom_jitter(data=data_peat,aes(x=dry,y=Balticum_prop), -->
<!--                 position = position_jitter(0.1,0.01), -->
<!--                 size=3,alpha=0.3,shape=16,color="darkturquoise")+ -->
<!--     geom_point(data=data.frame(ggemmeans(mod_abund_Balticum, -->
<!--                                          type="fixed",terms=c("dry"))), -->
<!--                aes(x=x,y=predicted),size=4,shape=16)+ -->
<!--     geom_errorbar(data=data.frame(ggemmeans(mod_abund_Balticum, -->
<!--                                             type="fixed",terms=c("dry"))), -->
<!--                   aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--                   width=0.2,size=0.5)+ -->
<!--     my_theme()+xlab("Dry period")+ylab("Balticum abundance")+ -->
<!--   theme(axis.text.y = element_blank(), -->
<!--             axis.title.y = element_blank(), -->
<!--             plot.margin = margin(r = 10, l = 5,t=10,b=10)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- figure4_b<-ggarrange(figure4_b_1,figure4_b_2,figure4_b_3,nrow=1) -->
<!-- figure4_d<-ggarrange(figure4_d_1,figure4_d_2,nrow=1) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- figure4<-cowplot::plot_grid( -->
<!--   cowplot::plot_grid(figure4_a,figure4_b,ncol=2,labels=c("A)","B)"), -->
<!--             label_fontfamily="serif",rel_widths=c(0.3,0.7))+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   cowplot::plot_grid(figure4_c,figure4_d,ncol=2,labels=c("C)","D)"), -->
<!--             label_fontfamily="serif",rel_widths=c(0.35,0.65))+ -->
<!--     theme(plot.background=element_rect(fill="white", color = NA)), -->
<!--   nrow=2) -->
<!-- figure4 -->
<!-- ggsave(filename="output/figures/figure4.tiff",plot=figure4, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ggsave(filename="output/figures/figure4.pdf",plot=figure4, -->
<!--        width=28,height=21,units="cm",dpi=300) -->
<!-- ``` -->

<!-- ## OLD: Figure 5: interactions -->

<!-- ```{r} -->
<!-- figure5<-cowplot::plot_grid(plot_sphagnum_int,plot_Erica_int,ncol=2, -->
<!--                             labels=c("A)","B)"),label_fontfamily="serif") -->
<!-- figure5 -->
<!-- ggsave(filename="output/figures/figure5.tiff",plot=figure5, -->
<!--        width=24,height=12,units="cm",dpi=300) -->
<!-- ggsave(filename="output/figures/figure5.pdf",plot=figure5, -->
<!--        width=24,height=12,units="cm",dpi=300) -->
<!-- ``` -->

## Figure 2: Plant gropus

Create average predictions

```{r}
# Create average line among factors=0 and factors=1
average_prediction_tot_Sphagnum_temp<-rbind(
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_tot_Sphagnum_nutrient<-rbind(
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_tot_Sphagnum_temp,type="zi_prob",
                   terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
figure2_a_1<-
  # Total Sphagnum presence ~ temp
  ggplot()+
  geom_ribbon(data=average_prediction_tot_Sphagnum_temp,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_tot_Sphagnum_temp,
            aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=temp,y=tot_Sphagnum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Probability of total Sphagnum presence")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure2_a_2<-
  # Total Sphagnum presence ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=tot_Sphagnum_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=average_prediction_tot_Sphagnum_nutrient,
             aes(x=x,y=1-predicted),size=4,shape=16)+
  geom_errorbar(data=average_prediction_tot_Sphagnum_nutrient,
                    aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8,1))+
  my_theme()+xlab("Nutrient input")+
  ylab("Probability of total Sphagnum presence") +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure2_b_1<-
  # Total Sphagnum abundance ~ temp
  ggplot()+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                        type="fixed",terms=c("temp[all]"))),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                      type="fixed",terms=c("temp[all]"))),
            aes(x=x,y=predicted))+
  geom_point(data=data_peat,aes(x=temp,y=tot_Sphagnum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Total Sphagnum abundance")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure2_b_2<-
  # Total Sphagnum abundance ~ nutr
  ggplot()+
      geom_jitter(data=data_peat,aes(x=nutrient,y=tot_Sphagnum_prop),
                  position = position_jitter(0.1,0.01),
                  size=3,alpha=0.3,shape=16,color="darkturquoise")+
      geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                           type="fixed",terms=c("nutrient"))),
                 aes(x=x,y=predicted),size=4,shape=16)+
      geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                              type="fixed",terms=c("nutrient"))),
                    aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                    width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+
      my_theme()+xlab("Nutrient input")+ylab("Total Sphagnum abundance")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure2_b_3<-
  # Total Sphagnum abundance ~ dry
  ggplot()+
  geom_jitter(data=data_peat,aes(x=dry,y=tot_Sphagnum_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                       type="fixed",terms=c("dry"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_tot_Sphagnum_temp,
                                          type="fixed",terms=c("dry"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8,1))+
  my_theme()+xlab("Dry period")+ylab("Total Sphagnum abundance") + 
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure2_c_1<-
  # Erio abundance ~ temp
  ggplot()+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                        type="fixed",terms=c("temp[all]"))),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                      type="fixed",terms=c("temp[all]"))),
            aes(x=x,y=predicted))+
  geom_point(data=subset(data_peat,Erio_prop>0),aes(x=temp,y=Erio_prop),
                 size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Erio abundance")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure2_c_2<-
  # Erio abundance ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Erio_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                       type="fixed",terms=c("nutrient"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                          type="fixed",terms=c("nutrient"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+
  my_theme()+xlab("Nutrient input")+ylab("Erio abundance")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure2_c_3<-
  # Erio abundance ~ dry
  ggplot()+
  geom_jitter(data=data_peat,aes(x=dry,y=Erio_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                       type="fixed",terms=c("dry"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Erio_nozi_temp,
                                          type="fixed",terms=c("dry"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+
  my_theme()+xlab("Dry period")+ylab("Erio abundance")+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure2_d_1<-
  # Erica abundance ~ temp
  ggplot()+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_Erica_nozi_temp,
                                        type="fixed",terms=c("temp[all]"))),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_Erica_nozi_temp,
                                      type="fixed",terms=c("temp[all]"))),
            aes(x=x,y=predicted))+
  geom_point(data=subset(data_peat,Erica_prop>0),aes(x=temp,y=Erica_prop),
                 size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Erica abundance")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure2_e_1<-
  # Carex abundance ~ nutr
   ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Carex_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi_temp,
                                       type="fixed",terms=c("nutrient"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi_temp,
                                          type="fixed",terms=c("nutrient"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+
  my_theme()+xlab("Nutrient input")+ylab("Carex abundance")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10))
figure2_e_2<-
  # Carex abundance ~ dry
  ggplot()+
  geom_jitter(data=data_peat,aes(x=dry,y=Carex_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Carex_nozi_temp,
                                       type="fixed",terms=c("dry"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Carex_nozi_temp,
                                          type="fixed",terms=c("dry"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8))+
  my_theme()+xlab("Dry period")+ylab("Carex abundance")+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
```

```{r}
figure2_a<-ggarrange(# Total Sphagnum presence
  figure2_a_1,figure2_a_2,nrow=1)
figure2_b<-ggarrange(# Total Sphagnum abundance
  figure2_b_1,figure2_b_2,figure2_b_3,nrow = 1)
figure2_c<-ggarrange(# Erio
  figure2_c_1,figure2_c_2,figure2_c_3,nrow=1)
figure2_d<-ggarrange(# Erica
  figure2_d_1+theme(plot.margin=margin(l = 5,t=10,b=10)),nrow = 1)
figure2_e<-ggarrange(# Carex
  figure2_e_1,figure2_e_2,nrow=1)
```

```{r}
figure2_alternative<-
  cowplot::plot_grid(
    cowplot::plot_grid(figure2_a,figure2_b,figure2_c,ncol=1,
    labels=c("A)","B)","C)"),label_fontfamily="serif"),
    cowplot::plot_grid(figure2_d,figure2_e,ncol=2,labels=c("D)","E)"),
                       label_fontfamily="serif",rel_widths=c(0.35,0.65)),ncol=1,
    rel_heights=c(0.75,0.25))
figure2_alternative
ggsave(filename="output/figures/figure2_alternative.tiff",
       plot=figure2_alternative,width=25,height=40,units="cm",dpi=300)
ggsave(filename="output/figures/figure2_alternative.pdf",
       plot=figure2_alternative,width=40,height=40,units="cm",dpi=300)
```


```{r}
figure2<-cowplot::plot_grid(
  cowplot::plot_grid(figure2_a,figure2_b,ncol=2,labels=c("A)","B)"),
            label_fontfamily="serif")+
    theme(plot.background=element_rect(fill="white", color = NA)),
  cowplot::plot_grid(figure2_c,figure2_d,figure2_e,ncol=3,
                     labels=c("C)","D)","E)"),
            label_fontfamily="serif",rel_widths=c(0.50,0.17,0.33))+
    theme(plot.background=element_rect(fill="white", color = NA)),
  nrow=2)
figure2
ggsave(filename="output/figures/figure2.tiff",plot=figure2,
       width=40,height=25,units="cm",dpi=300)
ggsave(filename="output/figures/figure2.pdf",plot=figure2,
       width=40,height=25,units="cm",dpi=300)
```

## Figure 3: Selected Sphagnum species: Fuscum and Rubellum

Create average predictions

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Fuscum_moist<-rbind(
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%  # NaNs produced
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Fuscum_nutrient<-rbind(
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Fuscum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Rubellum_moist<-rbind(
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("moist[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%  # NaNs produced
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Rubellum_nutrient<-rbind(
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Rubellum_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
``` 

```{r}
figure3_a_1<-
  # Fusum presence ~ moist
  ggplot()+
  geom_ribbon(data=average_prediction_Fuscum_moist,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_Fuscum_moist,aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=moist,y=Fuscum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Moisture")+ylab("Probability of Fuscum presence")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure3_a_2<-
  # Fusum presence ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Fuscum_prop),
              position=position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=average_prediction_Fuscum_nutrient,
             aes(x=x,y=1-predicted),size=4,shape=16)+
  geom_errorbar(data=average_prediction_Fuscum_nutrient,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Nutrient input")+ylab("Probability of Fuscum presence")+
  theme(axis.text.y = element_blank(),axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure3_b_1<-
  # Fuscum abundance ~ temp
  ggplot()+
  geom_ribbon(data=data.frame(ggemmeans(mod_abund_Fuscum_temp,
                                        type="fixed",terms=c("temp"))),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),alpha=0.2)+
  geom_line(data=data.frame(ggemmeans(mod_abund_Fuscum_temp,
                                      type="fixed",terms=c("temp"))),
            aes(x=x,y=predicted))+
  geom_point(data=data_peat,aes(x=temp,y=Fuscum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Fuscum abundance")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure3_b_2<-
  # Fuscum abundance ~ dry
  ggplot()+
  geom_jitter(data=data_peat,aes(x=dry,y=Fuscum_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Fuscum_temp,
                                       type="fixed",terms=c("dry"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Fuscum_temp,
                                          type="fixed",terms=c("dry"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Dry period")+ylab("Fuscum abundance")+
  theme(axis.text.y = element_blank(),axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure3_c_1<-
  # Rubellum presence ~ moist
  ggplot()+
  geom_ribbon(data=average_prediction_Rubellum_moist,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_Rubellum_moist,aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=moist,y=Rubellum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Moisture")+ylab("Probability of Rubellum presence")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )
figure3_c_2<-
  # Rubellum presence ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Rubellum_prop),
              position=position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=average_prediction_Rubellum_nutrient,
             aes(x=x,y=1-predicted),size=4,shape=16)+
  geom_errorbar(data=average_prediction_Rubellum_nutrient,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Nutrient input")+ylab("Probability of Rubellum presence")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )+
  theme(axis.text.y = element_blank(),axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure3_d_1<-
  # Rubellum abundance ~ fire
  ggplot()+
  geom_jitter(data=data_peat,aes(x=fire,y=Rubellum_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Rubellum_temp,
                                       type="fixed",terms=c("fire"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Rubellum_temp,
                                          type="fixed",terms=c("fire"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Fire")+ylab("Rubellum abundance")+
  theme(plot.margin=margin(r = 10,l = 5,t=10,b=10))
```

```{r}
figure3_a<-ggarrange(figure3_a_1,figure3_a_2,nrow=1)
figure3_b<-ggarrange(figure3_b_1,figure3_b_2,nrow=1)
figure3_c<-ggarrange(figure3_c_1,figure3_c_2,nrow=1)
```

```{r}
figure3<-cowplot::plot_grid(
  cowplot::plot_grid(figure3_a,figure3_b,ncol=2,labels=c("A)","B)"),
            label_fontfamily="serif")+
    theme(plot.background=element_rect(fill="white", color = NA)),
  cowplot::plot_grid(figure3_c,figure3_d,ncol=2,labels=c("C)","D)"),
            label_fontfamily="serif",rel_widths=c(0.64,0.36))+
    theme(plot.background=element_rect(fill="white", color = NA)),
  nrow=2)
figure3
ggsave(filename="output/figures/figure3.tiff",plot=figure3,
       width=28,height=21,units="cm",dpi=300)
ggsave(filename="output/figures/figure3.pdf",plot=figure3,
       width=28,height=21,units="cm",dpi=300)
```

## Figure 4: Selected Sphagnum species: Medium, Balticum and Cuspidata

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Medium_temp<-rbind(
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Medium_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Balticum_temp<-rbind(
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Balticum_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Cuspidata_temp<-rbind(
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="d"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="e"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="f"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=0,fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="g"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("temp[all]"),
                   condition=c(nutrient=1,fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="h")
)%>%
  group_by(x)%>%summarise(predicted=mean(predicted),std.error=mean(std.error),
                          conf.low=mean(conf.low),conf.high=mean(conf.high))
```

```{r}
# Create average line among factors=0 and factors=1
average_prediction_Cuspidata_nutrient<-rbind(
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=1)))%>%
    select(-group)%>%mutate(type="a"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=0)))%>%
    select(-group)%>%mutate(type="b"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=0,dry=1)))%>%
    select(-group)%>%mutate(type="c"),
  tibble(ggpredict(mod_abund_Cuspidata_temp,type="zi_prob",terms=c("nutrient"),
                   condition=c(fire=1,dry=0)))%>%
    select(-group)%>%mutate(type="d")
  )%>%
  group_by(x)%>%summarise(predicted=mean(predicted),
                          std.error=mean(std.error,na.rm=T),
                          conf.low=mean(conf.low,na.rm=T),
                          conf.high=mean(conf.high,na.rm=T))
```

```{r}
figure4_a<-
  # Medium presence ~ temp
  ggplot()+
  geom_ribbon(data=average_prediction_Medium_temp,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_Medium_temp,aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=temp,y=Medium_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Probability of Medium presence")+
  theme(plot.margin=margin(l = 5,t=10,b=10))
figure4_b_1<-
  # Medium abundance ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Medium_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                         type="fixed",terms=c("nutrient"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                          type="fixed",terms=c("nutrient"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Nutrient input")+ylab("Medium abundance")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10))
figure4_b_2<-
  # Medium abundance ~ fire
  ggplot()+
  geom_jitter(data=data_peat,aes(x=fire,y=Medium_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                       type="fixed",terms=c("fire"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                          type="fixed",terms=c("fire"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Fire")+ylab("Medium abundance")+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure4_b_3<-
  # Medium abundance ~ dry
  ggplot()+
  geom_jitter(data=data_peat,aes(x=dry,y=Medium_prop),
              position = position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                       type="fixed",terms=c("dry"))),
             aes(x=x,y=predicted),size=4,shape=16)+
  geom_errorbar(data=data.frame(ggemmeans(mod_abund_Medium_temp,
                                          type="fixed",terms=c("dry"))),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Dry period")+ylab("Medium abundance")+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
figure4_c<-
  # Balticum presence ~ temp
  ggplot()+
  geom_ribbon(data=average_prediction_Balticum_temp,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_Balticum_temp,aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=temp,y=Balticum_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Probability of Balticum presence")+
  theme(plot.margin=margin(l = 5,t=10,b=10))
figure4_d_1<-
  # Cuspidata presence ~ temp
  ggplot()+
  geom_ribbon(data=average_prediction_Cuspidata_temp,
              aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
              alpha=0.2)+
  geom_line(data=average_prediction_Cuspidata_temp,aes(x=x,y=1-predicted))+
  geom_point(data=data_peat,aes(x=temp,y=Cuspidata_prop),
             size=3,alpha=0.3,shape=16,color="darkturquoise")+
  my_theme()+xlab("Temperature")+ylab("Probability of Cuspidata presence")+
  theme(plot.margin=margin(l = 5,t=10,b=10))
figure4_d_2<-
  # Cuspidata presence ~ nutr
  ggplot()+
  geom_jitter(data=data_peat,aes(x=nutrient,y=Cuspidata_prop),
              position=position_jitter(0.1,0.01),
              size=3,alpha=0.3,shape=16,color="darkturquoise")+
  geom_point(data=average_prediction_Cuspidata_nutrient,
             aes(x=x,y=1-predicted),size=4,shape=16)+
  geom_errorbar(data=average_prediction_Cuspidata_nutrient,
                aes(x=x,y=1-predicted,ymin=1-conf.low,ymax=1-conf.high),
                width=0.2,size=0.5)+
  my_theme()+xlab("Nutrient input")+ylab("Probability of Cuspidata presence")+
  theme(plot.margin = margin(l=10,r = 5,t=10,b=10) )+
  theme(axis.text.y = element_blank(),axis.title.y = element_blank(),
        plot.margin = margin(r = 10, l = 5,t=10,b=10))
```

```{r}
figure4_b<-ggarrange(figure4_b_1,figure4_b_2,figure4_b_3,nrow=1)
figure4_d<-ggarrange(figure4_d_1,figure4_d_2,nrow=1)
```

```{r}
figure4<-cowplot::plot_grid(
  cowplot::plot_grid(figure4_a,figure4_b,ncol=2,labels=c("A)","B)"),
            label_fontfamily="serif",rel_widths=c(0.3,0.7))+
    theme(plot.background=element_rect(fill="white", color = NA)),
  cowplot::plot_grid(figure4_c,figure4_d,ncol=2,labels=c("C)","D)"),
            label_fontfamily="serif",rel_widths=c(0.35,0.65))+
    theme(plot.background=element_rect(fill="white", color = NA)),
  nrow=2)
figure4
ggsave(filename="output/figures/figure4.tiff",plot=figure4,
       width=28,height=21,units="cm",dpi=300)
ggsave(filename="output/figures/figure4.pdf",plot=figure4,
       width=28,height=21,units="cm",dpi=300)
```

## Figure 5: interactions

```{r}
figure5<-cowplot::plot_grid(plot_sphagnum_int,plot_Erica_int,
                            plot_Erio_int,ncol=3,
                            labels=c("A)","B)","C)"),label_fontfamily="serif")
figure5
ggsave(filename="output/figures/figure5.tiff",plot=figure5,
       width=35,height=12,units="cm",dpi=300)
ggsave(filename="output/figures/figure5.pdf",plot=figure5,
       width=35,height=12,units="cm",dpi=300)
```

# R session info

```{r}
sessionInfo()
```





